### 2024-06-12 tex/description.tex
Add description

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling thm-restate support, use "thm-restate"

\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

\graphicspath{{./fig/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{OCMu64: a solver for One-sided Crossing Minimization} %TODO Please add

%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

\author{Ragnar {Groot Koerkamp}}{ETH Zurich, Switzerland}{ragnar.grootkoerkamp@gmail.com}{https://orcid.org/0000-0002-2091-1237}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

\author{Mees de Vries}{}{}{}{}

\authorrunning{R. Groot Koerkamp and M. de Vries} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Ragnar Groot Koerkamp and Mees de Vries} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[500]{Theory of computation~Mathematical optimization}
\ccsdesc[300]{Theory of computation~Computational geometry}

\keywords{Graph drawing, crossing number, branch and bound} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional

\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
\supplementdetails[subcategory={Source Code}]{Software}{https://github.com/mjdv/ocmu64} %linktext, cite, and subcategory are optional

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

%% \acknowledgements{I want to thank \dots}%optional

\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \EventEditors{John Q. Open and Joan R. Access}
%% \EventNoEds{2}
%% \EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
%% \EventShortTitle{CVIT 2016}
%% \EventAcronym{CVIT}
%% \EventYear{2016}
%% \EventDate{December 24--27, 2016}
%% \EventLocation{Little Whinging, United Kingdom}
%% \EventLogo{}
%% \SeriesVolume{42}
%% \ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\R}{\mathbb R}
\renewcommand{\b}{\prec}
\newcommand{\be}{\preceq}
\newcommand{\g}{\sim}
\renewcommand{\u}{\overline{u}}
\renewcommand{\v}{\overline{v}}
\newcommand{\w}{\overline{w}}

\begin{document}

\maketitle

%TODO mandatory: add short abstract of the document
\begin{abstract}
  Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization} (OCM) problem is to find an order of the
  vertices of $B$ that minimizes the number
  of edge crossings when drawn in the plane.

  We prove a number of novel reductions, and apply these in our solver OCMu64 that
  uses branch-and-bound on the order of the vertices of $B$.
\end{abstract}

\section{Introduction}

The 2024 edition of PACE, an annual optimization challenge, considers the
\emph{one-sided crossing minimization} problem, defined as follows.
Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
$(0, i)$ and $(1,j)$ for components $A$ and $B$ respectively. The order of $A$
is fixed, and the goal is the find an order of $B$ that minimizes the number of
crossings when edges are drawn as straight lines.

We introduce some new reductions and overview our algorithm. Proofs are brief or
omitted due to lack of space.

\section{Definitions}
Since the order of $A$ is fixed, we set $A=\{0, \dots, [A]\}$ (where $[n]=\{0,\dots,n-1\}$) and draw the
vertices in this order.
Let $u, v\in B$ be two vertices in $B$. Then $N(u),N(v)\subseteq A$ are their sets of
neighbours.
We write $c(u,v)=\sum_{a\in N(u)}\sum_{b\in N(v)} [a>b]$ for the number of crossings between edges from $u$ and $v$
when $u$ is drawn before $v$. For $X,Y\subseteq B$ we set
$c(X,Y) = \sum_{x\in X}\sum_{y\in Y} c(x,y)$ for the cost of ordering all
vertices of $X$ before all vertices of $Y$.
More generally, $c(X,Y,Z) = c(X, Y) + c(X, Z) + c(Y, Z)$.
We also consider the \emph{reduced cost} $r(X,Y) = c(X, Y) - c(Y, X)$, which is
negative when $X$ is better \emph{before} $Y$ and positive when $X$ is better \emph{after} $Y$.

We write $u\b v$ when $u$ must come before $v$ in all minimal solutions and
$u\be v$ when there exist minimal solutions where $u$ comes before $v$, and we
call such $(u,v)$ \emph{dominating pairs}.
We write $u\g v$ when there is a minimal solution where $u$ and $v$ are
consecutive, in that order.

The following result is well known.

% TODO: Citation
\begin{observation}\label{lem:weak}
  When all neighbours of $u$ come before all neighbours of $v$, then $u$ goes
  before $v$. I.e., when $\max N(u) \leq \min N(v)$, then $u\be v$.
  When additionally ${\min N(u) < \max N(v)}$, then $u\b v$.
\end{observation}

\section{Methods}
\subsection{Reductions}
\subparagraph{Dominating pairs}
We give a much stronger version of \cref{lem:weak}. In fact, this
lemma is as strong as can be when only considering $N(u)$ and $N(v)$.

\begin{lemma}[Strong dominating pair]\label{lem:sdp}
  Write $n:= |N(u)|$, $m:=|N(v)|$, and consider both sets as sorted lists.
  When for all $i\in [n]$ we have
  $ N(u)_i \leq N(v)_{\lfloor i\cdot m/n \rfloor} $,
  then $u\be v$.
  When there is an $i$ such that the inequality is strict, then $u\b v$.
\end{lemma}

%Note that the condition is equivalent to the symmetric version: for all $j\in [m]$:
%$ U_{\lceil j\cdot n/m \rceil} \leq V_j $.

\begin{proof}
  Consider for each $u\in B$ the function $w_u: A\to \R_{\geq 0}$ that
  assigns \emph{weight} $1$ to neighbours of $u$ and weight $0$ otherwise.
  Let $W_u = \sum_{a\in A} w_u(A)$ be the total weight (degree) of $u$.
  Then for any $u$ and $v$, $c(u,v) = \sum_{a,b\in A, a>b} w_u(a) \cdot w_v(b)$.
  We can `shift' some weight $\delta$ of $w_u$ to the right from $a_1$ to $a_2>a_1$ by
  decreasing $w_u(a_1)\geq \delta$ by $\delta$ and increasing $w_u(a_2)$ by
  $\delta$.
  This increases the value of
  $c(u,v)$ by $\delta \cdot \sum_{a_1 < b \leq a_2} w_b(v)\geq 0$.

  Consider \emph{scaled} functions $\w_u = w_u / W_u$ and $\w_v = w_v / W_v$.
  We have $c(u,v) = W_u\cdot W_v\cdot c(\u, \v)$ and $c(v,u) = W_u\cdot
  W_v\cdot c(\v, \u)$, so that the sign of $r(u,v) = W_u\cdot W_v\cdot
  r(\w_u, \w_v)$ is independent of scaling.
  The condition in the lemma holds if and only if $\w_u$ can be transformed into
  $\w_v$ by shifting weight to the right.

  Now suppose there is an optimal solution where $v$ occurs before $x$:
  $(\dots, v, x_1, \dots, x_k, u, \dots)$.
  We set $X=(x_1,\dots, x_k)$ and write $w_X=\sum_{i=1}^k w_i$ for the combined weight of the
  neighbours of the $x_i$.
  Since the solution is optimal, we have $r(v,X) \leq 0$ and $r(X, u) \leq 0$,
  and hence $r(\v, X)\leq 0$ and $r(X, \u) \leq 0$.
  Since we can go from $\w_u$ to $\w_v$ by shifting weight to the right, we have
  $r(\u, X) \leq r(\v, X)$. We get $0 \leq -r(X, \u) = r(\u, X) \leq r(\v, X)
  \leq 0$. Thus, all must equal $0$, and $(v, X, u)$ is as good as $(v, u, X)$. By a
  similar argument we can swap $u$ and $v$ to obtain $(u, v, X)$. We conclude
  $u\be v$.
  When one of the inequalities in the condition is strict that implies $c(u,v) <
  c(v,u)$ and we have $u\b v$.
\end{proof}

\begin{remark}
  When the condition in \cref{lem:sdp} does not hold, there exists a multiset
  $\mathcal X\subseteq A$ such that $v, \mathcal X, u$ is the optimal order.
\end{remark}

Although such a set $\mathcal X$ may exist in theory, it does not have to exist in
practice, motivating the following definition.

\begin{lemma}[Practical dominating pair]\label{pdp}
  Suppose $r(u,v)\leq 0$.
  A \emph{blocking} set $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u)$ is
  stricly better than both $c(u,v,X)$ and $c(X,u,v)$.
  If there is no blocking set, then $u\be v$.
\end{lemma}

In practice, such a set $X$ can be found, if one exists, using knapsack: for
each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a
subset summing to ${\leq{}(r(u, v), r(u, v))}$.

Note that we do not require $(v, X, u)$ to be a true local minimum, since we do
not consider interactions between vertices in $X$, as that would make finding
such sets much harder.

\subparagraph{Gluing}
We now turn our attention to \emph{gluing}, i.e., proving that two vertices $u$
and $v$ always go right next to each other. We start with a simple case of
\emph{gluing to the front}.

\begin{lemma}[Greedy]\label{greedy}
  When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
  starts with $u$.
\end{lemma}

\begin{remark}
  Let $u$ and $v$ satisfy $r(u,v) \leq 0$.
  When $N(u)=N(v)$ or more generally $\w_u=\w_v$, we can glue $u$ and $v$: $u\g v$.
  Otherwise, there is a multiset $\mathcal X\subseteq A$ such that $(u, X, v)$ is
  better than $(u,v,X)$ and $(X,u,v)$.
\end{remark}
This means that there is no `strong gluing'.
\begin{lemma}[Practical gluing]\label{pg}
  Let $u$ and $v$ satisfy $r(u,v)\leq 0$ and $u\be v$.
  A subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is strictly
  better than $c(u,v,X)$ and $c(X,u,v)$.
  If there is no blocking set, then $u \g v$.
\end{lemma}
Again such sets $X$ can be found or proven to not exist using a knapsack
algorithm: add points $P_x = (r(u, x), r(x, v))$ and search for a non-empty
set summing to $\leq{}(0,0)$.

\begin{remark}[Tail variants]
  Our branch-and-bound method fixes vertices of the
solution from left to right. That means that at each step \cref{pg,pdp} can be applied to
just the \emph{tail}.
\end{remark}

\subsection{Branch-and-bound}
Our solver \texttt{OCMu64} is based on a standard branch-and-bound on the order the solution.
We start with fixed prefix $P=()$ and tail $T=B$, and in each step we try (a
subset of) all vertices in $T$ as the next vertex appended to $P$.
In a preprocessing step we compute the trivial lower bound $S_0 =
\sum_{u,v}\min(c(u,v),c(v,u))$ on the score.
We keep track of the score $S_P$ of the prefix and $S_{PT}=c(P, T)$ of
prefix-tail intersections, and abort when this score goes above the best
solution found so far. The \emph{excess} of a tail is its optimal score above
the trivial lower bound. We do a number of optimizations.

\begin{description}
  \item[Graph simplification] We drop degree-$0$ vertices, merge identical
    vertices, and split the graph into \emph{independent} components when
    possible. We find an initial solution using local search that tries to move
    slices and optimally insert them, and re-label all nodes accordingly to make
    memory accesses more efficient.
  \item[Dominating pairs] We find all dominating pairs and store them. For the
    exact track we also find practical dominating pairs. Instances for the parameterized
    track are simple enough that the overhead was not worth it. Also for each
    tail we search for new `tail-local' practical dominating pairs. In each state, we only
    try vertices $u\in T$ not dominated by another $v\in T$.
  \item[Gluing] We use the greedy strategy \cref{greedy}. Our implementation
    of \cref{pg} contained a bug, so we did not use this. (Also benefits
    seemed limited.)
  \item[Tail cache] In each step, we search for the longest suffix of $T$ that
    has been seen before, and reuse (the lower bound on) its excess. We also
    cache the tail-local practical dominating pairs.
  \item[Optimal insert] Instead of simply appending $u$ to the end of $P$, we
    insert it in the optimal position.\footnote{The idea is simple, but the
    implementation is tricky because it interacts in complicated ways with
    the caching of results for each tail.}
\end{description}

\section{Discussion}
\texttt{OCMu64} is a simple branch-and-bound method for solving one-sided
crossing minimization that does not depend on advanced ILP or SAT solvers.

This also seems to be its biggest limitation: while LP methods can use
the dual-space, \texttt{OCMu64} only considers the primal space to find lower
bounds on subproblems.

\end{document}

### 2024-06-19 tex/description.tex
add DOI to description
Changes in description intro

@@
 
-\author{Mees de Vries}{}{}{}{}
+\author{Mees de Vries}{Unaffiliated, Netherlands}{meesdevries@protonmail.com}{}{}
 
@@
 
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+\relatedversion{\url{https://doi.org/10.5281/zenodo.11671980}} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
 %\relatedversiondetails[linktext={opt.
@@
 \newcommand{\w}{\overline{w}}
+\DeclareMathOperator{\supp}{supp}
 
@@
 Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
-$(0, i)$ and $(1,j)$ for components $A$ and $B$ respectively. The order of $A$
-is fixed, and the goal is the find an order of $B$ that minimizes the number of
+$(i, 1)$ and $(j,0)$ for components $A$ and $B$ respectively. The ordering of $A$
+is fixed, and the goal is the find an ordering of $B$ that minimizes the number of
 crossings when edges are drawn as straight lines.
 
-We introduce some new reductions and overview our algorithm. Proofs are brief or
+We introduce some new reductions and give an overview of our algorithm. Proofs are brief or
 omitted due to lack of space.
@@
 \section{Definitions}
-Since the order of $A$ is fixed, we set $A=\{0, \dots, [A]\}$ (where $[n]=\{0,\dots,n-1\}$) and draw the
-vertices in this order.
-Let $u, v\in B$ be two vertices in $B$. Then $N(u),N(v)\subseteq A$ are their sets of
-neighbours.
-We write $c(u,v)=\sum_{a\in N(u)}\sum_{b\in N(v)} [a>b]$ for the number of crossings between edges from $u$ and $v$
-when $u$ is drawn before $v$. For $X,Y\subseteq B$ we set
-$c(X,Y) = \sum_{x\in X}\sum_{y\in Y} c(x,y)$ for the cost of ordering all
-vertices of $X$ before all vertices of $Y$.
-More generally, $c(X,Y,Z) = c(X, Y) + c(X, Z) + c(Y, Z)$.
-We also consider the \emph{reduced cost} $r(X,Y) = c(X, Y) - c(Y, X)$, which is
-negative when $X$ is better \emph{before} $Y$ and positive when $X$ is better \emph{after} $Y$.
+We use $<$ to compare vertices in $A$ in their fixed ordering. We generalize to weighted graphs
+for the proof of \ref{lem:sdp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
+R^{\geq 0}$, where weight 0 is an absent edge. We write $c(u, v) = \sum_{(a, b) \in A^2}
+u(a)v(b)[a > b]$; in the unweighted case, this is the \emph{crossing number}, the number of
+crossings between edges incident to $u$ and $v$ when $u$ is drawn before $v$.
 
-We write $u\b v$ when $u$ must come before $v$ in all minimal solutions and
-$u\be v$ when there exist minimal solutions where $u$ comes before $v$, and we
-call such $(u,v)$ \emph{dominating pairs}.
-We write $u\g v$ when there is a minimal solution where $u$ and $v$ are
+For $X,Y\subseteq B$ we set $c(X,Y) = \sum_{x\in X}\sum_{y\in Y} c(x,y)$ for the cost of
+ordering all vertices of $X$ before all vertices of $Y$. More generally, $c(X,Y,Z) = c(X, Y) +
+c(X, Z) + c(Y, Z)$. We also consider the \emph{reduced cost} $r(X,Y) = c(X, Y) - c(Y, X)$,
+which is negative when $X$ is better \emph{before} $Y$ and positive when $X$ is better
+\emph{after} $Y$.
+
+We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
+is a \emph{fixed} pair. When there exists a minimal solution where $u$ comes before $v$, we
+write $u \be v$ and call $(u, v)$ \emph{weakly fixed}.
+We write $u\g v$ when there exists a minimal solution where $u$ and $v$ are
 consecutive, in that order.
@@
 \begin{observation}\label{lem:weak}
-  When all neighbours of $u$ come before all neighbours of $v$, then $u$ goes
-  before $v$. I.e., when $\max N(u) \leq \min N(v)$, then $u\be v$.
-  When additionally ${\min N(u) < \max N(v)}$, then $u\b v$.
+  When all neighbours of $u$ come before all neighbours of $v$, then $u$ goes before $v$. That
+    is, when $\max \supp (u) \leq \min \supp (v)$, then $u\be v$, and in fact $u \b v$ holds
+    unless $u$ and $v$ are both connected to only one and the same node in $A$.
 \end{observation}

### 2024-06-19 tex/description.tex
Change first lemma in description

@@
 We use $<$ to compare vertices in $A$ in their fixed ordering. We generalize to weighted graphs
-for the proof of \ref{lem:sdp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
-R^{\geq 0}$, where weight 0 is an absent edge. We write $c(u, v) = \sum_{(a, b) \in A^2}
+for the proof of \ref{lem:sfp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
+R^{\geq 0}$, where weight 0 is an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for the
+total weight of $u$, and set $\bar u = u/W_u$.
+
+We write $c(u, v) = \sum_{(a, b) \in A^2}
 u(a)v(b)[a > b]$; in the unweighted case, this is the \emph{crossing number}, the number of
-crossings between edges incident to $u$ and $v$ when $u$ is drawn before $v$.
-
-For $X,Y\subseteq B$ we set $c(X,Y) = \sum_{x\in X}\sum_{y\in Y} c(x,y)$ for the cost of
-ordering all vertices of $X$ before all vertices of $Y$. More generally, $c(X,Y,Z) = c(X, Y) +
-c(X, Z) + c(Y, Z)$. We also consider the \emph{reduced cost} $r(X,Y) = c(X, Y) - c(Y, X)$,
-which is negative when $X$ is better \emph{before} $Y$ and positive when $X$ is better
-\emph{after} $Y$.
+crossings between edges incident to $u$ and $v$ when $u$ is drawn before $v$.  For
+$X,Y\subseteq B$ we set $c(X,Y) = \sum_{x\in X}\sum_{y\in Y} c(x,y)$ for the cost of ordering
+all vertices of $X$ before all vertices of $Y$. More generally, $c(X,Y,Z) = c(X, Y) + c(X, Z) +
+c(Y, Z)$. We also consider the \emph{reduced cost} $r(X,Y) = c(X, Y) - c(Y, X)$, which is
+negative when $X$ is better \emph{before} $Y$ and positive when $X$ is better \emph{after} $Y$.
 
@@
 \subsection{Reductions}
-\subparagraph{Dominating pairs}
+\subparagraph{Fixed pairs}
 We give a much stronger version of \cref{lem:weak}. In fact, this
-lemma is as strong as can be when only considering $N(u)$ and $N(v)$.
+lemma is as strong as can be when only considering $u, v$ themselves. We begin with this
+abstract version, followed by a concrete corrolary.
 
-\begin{lemma}[Strong dominating pair]\label{lem:sdp}
-  Write $n:= |N(u)|$, $m:=|N(v)|$, and consider both sets as sorted lists.
-  When for all $i\in [n]$ we have
-  $ N(u)_i \leq N(v)_{\lfloor i\cdot m/n \rfloor} $,
-  then $u\be v$.
-  When there is an $i$ such that the inequality is strict, then $u\b v$.
+\begin{lemma}[Strong fixed pair]\label{lem:sfp}
+    Fix $u, v$. Suppose that for each $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
+    \leq b} \bar v(a)$. Then, for any $w$, we have $r(w, \bar v) \leq r(w, \bar u)$.
 \end{lemma}
 
-%Note that the condition is equivalent to the symmetric version: for all $j\in [m]$:
-%$ U_{\lceil j\cdot n/m \rceil} \leq V_j $.
+\begin{proof}
+    If $\bar u \neq \bar v$, consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
+    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Consider the transformation of
+    $\bar u$ which ``moves'' $\bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its successor
+    $a_1$, and call this transformed function $\bar u'$. Then
+    \[
+        r(w, \bar u') = r(w, \bar u) - ... \leq r(w, \bar u).
+    \]
+    Since $\bar v$ can be obtained from $\bar u$ by a finite sequence of such transformations,
+    the inequality follows.
+\end{proof}
 
+% To do, fix everything from here.
 \begin{proof}
@@
 \begin{remark}
-  When the condition in \cref{lem:sdp} does not hold, there exists a multiset
+  When the condition in \cref{lem:sfp} does not hold, there exists a multiset
   $\mathcal X\subseteq A$ such that $v, \mathcal X, u$ is the optimal order.

### 2024-06-20 tex/description.tex
More changes to description

@@
 R^{\geq 0}$, where weight 0 is an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for the
-total weight of $u$, and set $\bar u = u/W_u$.
+total weight of $u$, and set $\bar u = u/W_u$. Write $N(u) = \supp(u) \subseteq A$ for the
+set of neighbors of $u$.
 
@@
   When all neighbours of $u$ come before all neighbours of $v$, then $u$ goes before $v$. That
-    is, when $\max \supp (u) \leq \min \supp (v)$, then $u\be v$, and in fact $u \b v$ holds
+    is, when $\max N(u) \leq \min N(v)$, then $u\be v$, and in fact $u \b v$ holds
     unless $u$ and $v$ are both connected to only one and the same node in $A$.
@@
 
-\begin{lemma}[Strong fixed pair]\label{lem:sfp}
+\begin{lemma}[Strongly fixed pair]\label{lem:sfp}
     Fix $u, v$. Suppose that for each $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
@@
     \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Consider the transformation of
-    $\bar u$ which ``moves'' $\bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its successor
-    $a_1$, and call this transformed function $\bar u'$. Then
+    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
+    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
     \[
-        r(w, \bar u') = r(w, \bar u) - ... \leq r(w, \bar u).
+        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
     \]
@@
 
-% To do, fix everything from here.
+If $u \neq v$ satisfy the conditions of \ref{lem:sfp}, we call $(u, v)$ a \emph{strongly fixed
+pair}. Note that for such a pair, $r(u, v) < 0$.
+
+\begin{lemma}
+    If $(u, v)$ is a strongly fixed pair, then $u \b v$.
+\end{lemma}
 \begin{proof}
-  Consider for each $u\in B$ the function $w_u: A\to \R_{\geq 0}$ that
-  assigns \emph{weight} $1$ to neighbours of $u$ and weight $0$ otherwise.
-  Let $W_u = \sum_{a\in A} w_u(A)$ be the total weight (degree) of $u$.
-  Then for any $u$ and $v$, $c(u,v) = \sum_{a,b\in A, a>b} w_u(a) \cdot w_v(b)$.
-  We can `shift' some weight $\delta$ of $w_u$ to the right from $a_1$ to $a_2>a_1$ by
-  decreasing $w_u(a_1)\geq \delta$ by $\delta$ and increasing $w_u(a_2)$ by
-  $\delta$.
-  This increases the value of
-  $c(u,v)$ by $\delta \cdot \sum_{a_1 < b \leq a_2} w_b(v)\geq 0$.
-
-  Consider \emph{scaled} functions $\w_u = w_u / W_u$ and $\w_v = w_v / W_v$.
-  We have $c(u,v) = W_u\cdot W_v\cdot c(\u, \v)$ and $c(v,u) = W_u\cdot
-  W_v\cdot c(\v, \u)$, so that the sign of $r(u,v) = W_u\cdot W_v\cdot
-  r(\w_u, \w_v)$ is independent of scaling.
-  The condition in the lemma holds if and only if $\w_u$ can be transformed into
-  $\w_v$ by shifting weight to the right.
-
-  Now suppose there is an optimal solution where $v$ occurs before $x$:
-  $(\dots, v, x_1, \dots, x_k, u, \dots)$.
-  We set $X=(x_1,\dots, x_k)$ and write $w_X=\sum_{i=1}^k w_i$ for the combined weight of the
-  neighbours of the $x_i$.
-  Since the solution is optimal, we have $r(v,X) \leq 0$ and $r(X, u) \leq 0$,
-  and hence $r(\v, X)\leq 0$ and $r(X, \u) \leq 0$.
-  Since we can go from $\w_u$ to $\w_v$ by shifting weight to the right, we have
-  $r(\u, X) \leq r(\v, X)$. We get $0 \leq -r(X, \u) = r(\u, X) \leq r(\v, X)
-  \leq 0$. Thus, all must equal $0$, and $(v, X, u)$ is as good as $(v, u, X)$. By a
-  similar argument we can swap $u$ and $v$ to obtain $(u, v, X)$. We conclude
-  $u\be v$.
-  When one of the inequalities in the condition is strict that implies $c(u,v) <
-  c(v,u)$ and we have $u\b v$.
+    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
+    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
+    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, u) \leq 0$. But then $c(v,
+    X, u) \leq c(X, v, u) < c(X, u, v)$, a contradiction.
 \end{proof}
@@
 \begin{remark}
-  When the condition in \cref{lem:sfp} does not hold, there exists a multiset
-  $\mathcal X\subseteq A$ such that $v, \mathcal X, u$ is the optimal order.
+    Consider $u \neq v$ from the original, unweighted problem, taking only values $0, 1$. Let 
+    $n = |N(u)|, m = |N(v)|$, and consider both as ordered lists. Then $u, v$ are strongly
+    fixed if and only if for all $0 \leq i < n$,
+    \[
+        N(u)_i \leq N(v)_{\lfloor i\cdot m/n \rfloor},
+    \]
+    or equivalently for all $0 \leq j < m$, $N(u)_{\lceil j\cdot n/m \rceil} \leq N(v)_j$.
 \end{remark}
 
-Although such a set $\mathcal X$ may exist in theory, it does not have to exist in
-practice, motivating the following definition.
+\begin{remark}
+    Suppose that $u \neq v$ are not strongly fixed, and let $a_0 \in A$ be some element such
+    that $\sum_{a \leq a_0} \bar u(a) > \sum_{a \leq a_0} \bar v(a)$, and $a_1 \in A$ its
+    successor. By taking $X: A \to \mathbb R^{\geq 0}$ some function which assigns very high
+    weight to $a_1$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
+    \ref{lem:sfp} is optimal.
+\end{remark}
+This remark motivates the following: although such a function $X$ may exist in theory, it does
+not have to exist in the actual set $B$, motivating the following definition.
 
-\begin{lemma}[Practical dominating pair]\label{pdp}
+% todo from here
+\begin{lemma}[Practically fixed pair]\label{pfp}
   Suppose $r(u,v)\leq 0$.
@@
   Our branch-and-bound method fixes vertices of the
-solution from left to right. That means that at each step \cref{pg,pdp} can be applied to
+solution from left to right. That means that at each step \cref{pg,pfp} can be applied to
 just the \emph{tail}.

### 2024-06-20 tex/description.tex
Further changes to the description

@@
 
-% todo from here
 \begin{lemma}[Practically fixed pair]\label{pfp}
   Suppose $r(u,v)\leq 0$.
-  A \emph{blocking} set $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u)$ is
-  stricly better than both $c(u,v,X)$ and $c(X,u,v)$.
-  If there is no blocking set, then $u\be v$.
+    A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) < \min(c(v, u,
+    X), (X, v, u))$.  If there is no blocking set for $(u, v)$, then $u\b v$.
 \end{lemma}
 
-In practice, such a set $X$ can be found, if one exists, using knapsack: for
-each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a
-subset summing to ${\leq{}(r(u, v), r(u, v))}$.
+In practice, such a set $X$ can be found, if one exists, using a knapsack-like algorithm: for
+each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a subset summing
+to ${\leq{}(r(u, v), r(u, v))}$.
 
 Note that we do not require $(v, X, u)$ to be a true local minimum, since we do
-not consider interactions between vertices in $X$, as that would make finding
-such sets much harder.
+not consider interactions between vertices in $X$, as that would make ruling out the
+existence of such sets much harder.
 

### 2024-06-20 tex/description.tex
Minor changes again

@@
 
-\begin{lemma}[Strongly fixed pair]\label{lem:sfp}
-    Fix $u, v$. Suppose that for each $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
-    \leq b} \bar v(a)$. Then, for any $w$, we have $r(w, \bar v) \leq r(w, \bar u)$.
+\begin{definition}
+    If for every $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
+    \leq b} \bar v(a)$, and at least one of these inequalities is strict, we call $(u, v)$ a
+    \emph{strongly fixed pair}. Note that in this case $r(u, v) < 0$.
+\end{definition}
+\begin{lemma}[Strongly fixed pair]\label{lem:sfp} Take $u, v \in B$ a strongly fixed pair.
+    Then, for any $w$ we have $r(w, \bar v) \leq r(w, \bar u)$.
 \end{lemma}
-
 \begin{proof}
-    If $\bar u \neq \bar v$, consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
-    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Consider the transformation of
+    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
+    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
     $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
@@
 \end{proof}
-
-If $u \neq v$ satisfy the conditions of \ref{lem:sfp}, we call $(u, v)$ a \emph{strongly fixed
-pair}. Note that for such a pair, $r(u, v) < 0$.
-
 \begin{lemma}
-    If $(u, v)$ is a strongly fixed pair, then $u \b v$.
+    If $(u, v)$ is strongly fixed, then $u \b v$.
 \end{lemma}
@@
     solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
-    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, u) \leq 0$. But then $c(v,
-    X, u) \leq c(X, v, u) < c(X, u, v)$, a contradiction.
+    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u r(X,
+    u) \leq 0$. But then $c(v, X, u) \leq c(X, v, u) < c(X, u, v)$, a contradiction.
 \end{proof}

### 2024-06-20 tex/description.tex
Minor changes!
nits

@@
 \begin{definition}
-    If for every $b \in A$ we have $\sum_{a \leq b} \bar u(a) \geq \sum_{a
-    \leq b} \bar v(a)$, and at least one of these inequalities is strict, we call $(u, v)$ a
-    \emph{strongly fixed pair}. Note that in this case $r(u, v) < 0$.
+    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
+    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
+    is strict. This implies $r(u, v) {<} 0$.
 \end{definition}
-\begin{lemma}[Strongly fixed pair]\label{lem:sfp} Take $u, v \in B$ a strongly fixed pair.
-    Then, for any $w$ we have $r(w, \bar v) \leq r(w, \bar u)$.
+\begin{lemma}[Strongly fixed pair]\label{lem:sfp} When $u, v$ is a strongly fixed pair,
+    then for any $w: A\to \mathbb R^{\geq 0}$ we have $r(w, \bar v) \leq r(w, \bar u)$.
 \end{lemma}
@@
     \]
-    Since $\bar v$ can be obtained from $\bar u$ by a finite sequence of such transformations,
+    Since $\bar v$ can be obtained from $\bar u$ by a sequence of such transformations,
     the inequality follows.
@@
 \begin{proof}
-    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
+    Suppose by contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
     solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)

### 2024-06-20 tex/description.tex
nits
cref

@@
 We use $<$ to compare vertices in $A$ in their fixed ordering. We generalize to weighted graphs
-for the proof of \ref{lem:sfp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
+for the proof of \cref{lem:sfp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
 R^{\geq 0}$, where weight 0 is an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for the
@@
     \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u r(X,
-    u) \leq 0$. But then $c(v, X, u) \leq c(X, v, u) < c(X, u, v)$, a contradiction.
+    u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
+    contradicts $(v,X,u)$ being optimal.
 \end{proof}
@@
     successor. By taking $X: A \to \mathbb R^{\geq 0}$ some function which assigns very high
-    weight to $a_1$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
-    \ref{lem:sfp} is optimal.
+    weight to $a_0$ and $a_1$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
+    \cref{lem:sfp} is optimal.
 \end{remark}
-This remark motivates the following: although such a function $X$ may exist in theory, it does
+Although such a function $X$ may exist in theory, it does
 not have to exist in the actual set $B$, motivating the following definition.

### 2024-06-20 tex/description.tex
blocking set may have equality
simplify gluing to only \b variant

@@
 \newcommand{\be}{\preceq}
-\newcommand{\g}{\sim}
+\newcommand{\g}{\bullet}
 \renewcommand{\u}{\overline{u}}
@@
 We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
-is a \emph{fixed} pair. When there exists a minimal solution where $u$ comes before $v$, we
-write $u \be v$ and call $(u, v)$ \emph{weakly fixed}.
-We write $u\g v$ when there exists a minimal solution where $u$ and $v$ are
-consecutive, in that order.
+is a \emph{fixed} pair.
+We write $u\g v$ when $u$ and $v$ are consecutive in all minimal solutions.
 
@@
 \begin{observation}\label{lem:weak}
-  When all neighbours of $u$ come before all neighbours of $v$, then $u$ goes before $v$. That
-    is, when $\max N(u) \leq \min N(v)$, then $u\be v$, and in fact $u \b v$ holds
-    unless $u$ and $v$ are both connected to only one and the same node in $A$.
+  When all neighbours of $u$ come before all neighbours of $v$, then $u$ comes
+  before $v$ in any solution.
+  That is, when $\max N(u) \leq \min N(v)$ and $u\neq v$, then $u\b v$.
 \end{observation}
@@
   Suppose $r(u,v)\leq 0$.
-    A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) < \min(c(v, u,
+    A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) \leq \min(c(v, u,
     X), (X, v, u))$.  If there is no blocking set for $(u, v)$, then $u\b v$.
@@
 \begin{lemma}[Practical gluing]\label{pg}
-  Let $u$ and $v$ satisfy $r(u,v)\leq 0$ and $u\be v$.
-  A subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is strictly
-  better than $c(u,v,X)$ and $c(X,u,v)$.
+  Let $u$ and $v$ satisfy $r(u,v)\leq 0$ and $u\b v$.
+  A subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is at
+  least as good as $c(u,v,X)$ and $c(X,u,v)$.
   If there is no blocking set, then $u \g v$.

### 2024-06-20 tex/description.tex
non-empty
9+10

@@
 \begin{remark}
-  Let $u$ and $v$ satisfy $r(u,v) \leq 0$.
+  Let $u$ and $v$ satisfy $r(u,v) < 0$.
   When $N(u)=N(v)$ or more generally $\w_u=\w_v$, we can glue $u$ and $v$: $u\g v$.
-  Otherwise, there is a multiset $\mathcal X\subseteq A$ such that $(u, X, v)$ is
+  Otherwise, there is an $X : A\to \mathbb R^{\geq 0}$ such that $(u, X, v)$ is
   better than $(u,v,X)$ and $(X,u,v)$.
@@
 \begin{lemma}[Practical gluing]\label{pg}
-  Let $u$ and $v$ satisfy $r(u,v)\leq 0$ and $u\b v$.
-  A subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is at
+  Let $u$ and $v$ satisfy $u\b v$.
+  A non-empty subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is at
   least as good as $c(u,v,X)$ and $c(X,u,v)$.

### 2024-06-20 tex/description.tex
gluing

@@
 \renewcommand{\v}{\overline{v}}
-\newcommand{\w}{\overline{w}}
 \DeclareMathOperator{\supp}{supp}
@@
 \begin{remark}
-  Let $u$ and $v$ satisfy $r(u,v) < 0$.
-  When $N(u)=N(v)$ or more generally $\w_u=\w_v$, we can glue $u$ and $v$: $u\g v$.
-  Otherwise, there is an $X : A\to \mathbb R^{\geq 0}$ such that $(u, X, v)$ is
-  better than $(u,v,X)$ and $(X,u,v)$.
+  When $N(u)=N(v)$ or more generally $\bar u=\bar v$, we can glue $u$ and $v$: $u\g v$.
+  Otherwise when $r(u,v)\leq 0$, there is an $X : A\to \mathbb R^{\geq 0}$ such that $(u, X, v)$ is
+  strictly better than $(u,v,X)$ and $(X,u,v)$.
 \end{remark}

### 2024-06-20 tex/description.tex
shrink text

@@
     memory accesses more efficient.
-  \item[Dominating pairs] We find all dominating pairs and store them. For the
-    exact track we also find practical dominating pairs. Instances for the parameterized
+  \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
+    exact track we also find practical fixed pairs. Instances for the parameterized
     track are simple enough that the overhead was not worth it. Also for each
-    tail we search for new `tail-local' practical dominating pairs. In each state, we only
-    try vertices $u\in T$ not dominated by another $v\in T$.
-  \item[Gluing] We use the greedy strategy \cref{greedy}. Our implementation
+    tail we search for new `tail-local' practical fixed pairs. In each state, we only
+    try vertices $u\in T$ not fixed by another $v\in T$.
+  \item[Gluing] We use the greedy strategy of \cref{greedy}. Our implementation
     of \cref{pg} contained a bug, so we did not use this. (Also benefits
@@
   \item[Tail cache] In each step, we search for the longest suffix of $T$ that
-    has been seen before, and reuse (the lower bound on) its excess. We also
-    cache the tail-local practical dominating pairs.
-  \item[Optimal insert] Instead of simply appending $u$ to the end of $P$, we
+    was seen before, and reuse (the lower bound on) its excess. We also
+    cache the tail-local practical fixed pairs.
+  \item[Optimal insert] Instead of simply appending $u$ to $P$, we
     insert it in the optimal position.\footnote{The idea is simple, but the

### 2024-06-20 tex/description.tex
weak variatns
shrink

@@
 
+\begin{remark}[Weak variants]
+  It is also possible to consider \emph{weak} variants of the above lemmas that
+  only imply that $u<v$ or $u\g v$ in \emph{some} optimal solution. This requires careful
+  handling of cycles like $u\be v\be w\be u$ and $u\g v\g w\g u$.
+\end{remark}
+
 \begin{remark}[Tail variants]
   Our branch-and-bound method fixes vertices of the
-solution from left to right. That means that at each step \cref{pg,pfp} can be applied to
+solution from left to right. Thus, at each step \cref{pg,pfp} can be applied to
 just the \emph{tail}.

### 2024-06-20 tex/description.tex
Minor rephrasings.

@@
 for the proof of \cref{lem:sfp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
-R^{\geq 0}$, where weight 0 is an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for the
-total weight of $u$, and set $\bar u = u/W_u$. Write $N(u) = \supp(u) \subseteq A$ for the
+R^{\geq 0}$, where weight 0 represents an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for
+the total weight of $u$, and set $\bar u = u/W_u$. Write $N(u) = \supp(u) \subseteq A$ for the
 set of neighbors of $u$.
@@
 \subparagraph{Fixed pairs}
-We give a much stronger version of \cref{lem:weak}. In fact, this
-lemma is as strong as can be when only considering $u, v$ themselves. We begin with this
-abstract version, followed by a concrete corrolary.
-
+We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
+generalization possible when only considering $u, v$ themselves (see \cref{rem:strongest}).
 \begin{definition}
@@
     \]
-    Since $\bar v$ can be obtained from $\bar u$ by a sequence of such transformations,
+    Since $\bar v$ is obtained from $\bar u$ by a sequence of such transformations,
     the inequality follows.
@@
 \begin{proof}
-    Suppose by contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
+    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
     solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
@@
 
-\begin{remark}
-    Suppose that $u \neq v$ are not strongly fixed, and let $a_0 \in A$ be some element such
-    that $\sum_{a \leq a_0} \bar u(a) > \sum_{a \leq a_0} \bar v(a)$, and $a_1 \in A$ its
-    successor. By taking $X: A \to \mathbb R^{\geq 0}$ some function which assigns very high
-    weight to $a_0$ and $a_1$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
+\begin{remark}\label{rem:strongest}
+    Suppose that $u \neq v$ are not strongly fixed, and let $b \in A$ be some element such
+    that $\sum_{a \leq b} \bar u(a) > \sum_{a \leq b} \bar v(a)$. By taking $X: A \to \mathbb
+    R^{\geq 0}$ some function which assigns very high
+    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
     \cref{lem:sfp} is optimal.
@@
 
-\begin{lemma}[Practically fixed pair]\label{pfp}
+\begin{lemma}\label{pfp}
   Suppose $r(u,v)\leq 0$.
     A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) \leq \min(c(v, u,
-    X), (X, v, u))$.  If there is no blocking set for $(u, v)$, then $u\b v$.
+    X), (X, v, u))$.  If there is no blocking set for $(u, v)$, we call it a
+    \emph{practically fixed pair}, and $u\b v$.
 \end{lemma}

### 2024-06-20 tex/description.tex
Fix typo
drop discussion

@@
 \begin{abstract}
-  Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization} (OCM) problem is to find an order of the
-  vertices of $B$ that minimizes the number
-  of edge crossings when drawn in the plane.
+  Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization}
+  (OCM) problem is to find an order of the vertices of $B$ that minimizes the
+  number of edge crossings when drawn in the plane.
 
-  We prove a number of novel reductions, and apply these in our solver OCMu64 that
-  uses branch-and-bound on the order of the vertices of $B$.
+  We prove a number of novel reductions, and apply these in our solver OCMu64
+  that directly uses branch-and-bound on the order of the vertices of $B$ and
+  does not depend on ILP or SAT solvers.
 \end{abstract}
@@
 \subsection{Branch-and-bound}
-Our solver \texttt{OCMu64} is based on a standard branch-and-bound on the order the solution.
-We start with fixed prefix $P=()$ and tail $T=B$, and in each step we try (a
+Our solver \texttt{OCMu64} is based on a standard branch-and-bound on the ordering of the
+solution.  We start with fixed prefix $P=()$ and tail $T=B$, and in each step we try (a
 subset of) all vertices in $T$ as the next vertex appended to $P$.
@@
 \end{description}
-
-\section{Discussion}
-\texttt{OCMu64} is a simple branch-and-bound method for solving one-sided
-crossing minimization that does not depend on advanced ILP or SAT solvers.
-
-This also seems to be its biggest limitation: while LP methods can use
-the dual-space, \texttt{OCMu64} only considers the primal space to find lower
-bounds on subproblems.
-
 \end{document}

### 2024-06-20 tex/description.tex
More minor changes.

@@
 generalization possible when only considering $u, v$ themselves (see \cref{rem:strongest}).
-\begin{definition}
+\begin{definition}[Strongly fixed pair]
     We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
     \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
-    is strict. This implies $r(u, v) {<} 0$.
+    is strict. This implies $r(u, v) < 0$.
 \end{definition}
-\begin{lemma}[Strongly fixed pair]\label{lem:sfp} When $u, v$ is a strongly fixed pair,
-    then for any $w: A\to \mathbb R^{\geq 0}$ we have $r(w, \bar v) \leq r(w, \bar u)$.
+\begin{lemma}\label{lem:sfp} When $u, v$ is a strongly fixed pair,
+    then for any $w: A\to \mathbb R^{\geq 0}$ we have 
+    \[
+        r(w, \bar v) \leq r(w, \bar u).
+    \]
 \end{lemma}
@@
     solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
-    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u r(X,
-    u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
+    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u \cdot
+    r(X, u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
     contradicts $(v,X,u)$ being optimal.
@@
     $n = |N(u)|, m = |N(v)|$, and consider both as ordered lists. Then $u, v$ are strongly
-    fixed if and only if for all $0 \leq i < n$,
-    \[
-        N(u)_i \leq N(v)_{\lfloor i\cdot m/n \rfloor},
-    \]
-    or equivalently for all $0 \leq j < m$, $N(u)_{\lceil j\cdot n/m \rceil} \leq N(v)_j$.
+    fixed if and only if for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
+    \rfloor}$, which is how we check in practice whether $u, v$ is strongly fixed.
 \end{remark}
@@
 \begin{remark}\label{rem:strongest}
-    Suppose that $u \neq v$ are not strongly fixed, and let $b \in A$ be some element such
+    Suppose that $u, v \in B$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in
+    A$ be some element such
     that $\sum_{a \leq b} \bar u(a) > \sum_{a \leq b} \bar v(a)$. By taking $X: A \to \mathbb

### 2024-06-20 tex/description.tex
nits
inline footnote

@@
     fixed if and only if for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
-    \rfloor}$, which is how we check in practice whether $u, v$ is strongly fixed.
+    \rfloor}$ and at least one of the inequalities is strict, which is how we check in practice whether $u, v$ is strongly fixed.
 \end{remark}
@@
 \begin{lemma}\label{pfp}
-  Suppose $r(u,v)\leq 0$.
+  Suppose $r(u,v)< 0$.
     A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) \leq \min(c(v, u,
@@
 prefix-tail intersections, and abort when this score goes above the best
-solution found so far. The \emph{excess} of a tail is its optimal score above
+solution found so far. The \emph{excess} of a tail is its optimal score minus
 the trivial lower bound. We do a number of optimizations.
@@
   \item[Optimal insert] Instead of simply appending $u$ to $P$, we
-    insert it in the optimal position.\footnote{The idea is simple, but the
+    insert it in the optimal position. Note that the
     implementation is tricky because it interacts in complicated ways with
-    the caching of results for each tail.}
+    the caching of results for each tail.
 \end{description}

### 2024-06-22 tex/description.tex
Order => ordering, practical fixed => practically fixed

@@
   Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization}
-  (OCM) problem is to find an order of the vertices of $B$ that minimizes the
+  (OCM) problem is to find an ordering of the vertices of $B$ that minimizes the
   number of edge crossings when drawn in the plane.
@@
   We prove a number of novel reductions, and apply these in our solver OCMu64
-  that directly uses branch-and-bound on the order of the vertices of $B$ and
+  that directly uses branch-and-bound on the ordering of the vertices of $B$ and
   does not depend on ILP or SAT solvers.
@@
   \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
-    exact track we also find practical fixed pairs. Instances for the parameterized
+    exact track we also find practically fixed pairs. Instances for the parameterized
     track are simple enough that the overhead was not worth it. Also for each
-    tail we search for new `tail-local' practical fixed pairs. In each state, we only
+    tail we search for new `tail-local' practically fixed pairs. In each state, we only
     try vertices $u\in T$ not fixed by another $v\in T$.
@@
     was seen before, and reuse (the lower bound on) its excess. We also
-    cache the tail-local practical fixed pairs.
+    cache the tail-local practically fixed pairs.
   \item[Optimal insert] Instead of simply appending $u$ to $P$, we

### 2024-06-23 tex/description.tex
Minor language changes.
Remove the gluing notation, rewrite the gluing section.

@@
 We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
-is a \emph{fixed} pair.
-We write $u\g v$ when $u$ and $v$ are consecutive in all minimal solutions.
-
-The following result is well known.
+is a \emph{fixed} pair. The following result is well known.
 
@@
   before $v$ in any solution.
-  That is, when $\max N(u) \leq \min N(v)$ and $u\neq v$, then $u\b v$.
+  That is, when $\max N(u) \leq \min N(v)$ and $\bar u\neq \bar v$, then $u\b v$.
 \end{observation}
@@
     \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
-    is strict. This implies $r(u, v) < 0$.
+    is strict. Note that this implies $r(u, v) < 0$.
 \end{definition}
@@
 \end{proof}
-\begin{lemma}
+\begin{lemma}\label{lem:sfimplf}
     If $(u, v)$ is strongly fixed, then $u \b v$.
@@
 
+\begin{remark}[Weak variants]
+  It is also possible to consider \emph{weak} variants of the above lemmas that
+  only imply that $u < v$ in \emph{some} optimal solution. This requires careful
+  handling of cycles like $u\be v\be w\be u$.
+\end{remark}
+
 \subparagraph{Gluing}
 We now turn our attention to \emph{gluing}, i.e., proving that two vertices $u$
-and $v$ always go right next to each other. We start with a simple case of
-\emph{gluing to the front}.
-
-\begin{lemma}[Greedy]\label{greedy}
-  When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
-  starts with $u$.
-\end{lemma}
+and $v$ always go right next to each other, and we can treat them as a single vertex. First,
+let us see that we cannot get an analogous result to \cref{lem:sfimplf}.
 
 \begin{remark}
-  When $N(u)=N(v)$ or more generally $\bar u=\bar v$, we can glue $u$ and $v$: $u\g v$.
+  When $N(u)=N(v)$ in the unweighted case, or more generally $\bar u=\bar v$, we can glue $u$
+    and $v$.
   Otherwise when $r(u,v)\leq 0$, there is an $X : A\to \mathbb R^{\geq 0}$ such that $(u, X, v)$ is
@@
 \begin{lemma}[Practical gluing]\label{pg}
-  Let $u$ and $v$ satisfy $u\b v$.
-  A non-empty subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v)$ is at
-  least as good as $c(u,v,X)$ and $c(X,u,v)$.
-  If there is no blocking set, then $u \g v$.
+    Let $u$ and $v$ satisfy $r(u, v) \leq 0$.
+    A non-empty subset $X\subseteq B-\{u,v\}$ is \emph{blocking} when $c(u, X, v) \leq
+    \min(c(u, v, X), c(X, u, v))$. If there is no blocking set, then we can glue $u, v$.
 \end{lemma}
@@
 
-\begin{remark}[Weak variants]
-  It is also possible to consider \emph{weak} variants of the above lemmas that
-  only imply that $u<v$ or $u\g v$ in \emph{some} optimal solution. This requires careful
-  handling of cycles like $u\be v\be w\be u$ and $u\g v\g w\g u$.
-\end{remark}
+Let us also mention this gluing-like reduction: \emph{gluing to the front}.
+\begin{lemma}[Greedy]\label{greedy}
+  When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
+  starts with $u$.
+\end{lemma}
 

### 2024-06-24 tex/description.tex
move 'no strong gluing' remark
add some refs

@@
 We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
-is a \emph{fixed} pair. The following result is well known.
+is a \emph{fixed} pair. The following result is well known \cite[Fact 4]{dujmovic_2004}.
 
@@
 and $v$ always go right next to each other, and we can treat them as a single vertex. First,
-let us see that we cannot get an analogous result to \cref{lem:sfimplf}.
+let us see that we cannot get `strong gluing' result analogous to \cref{lem:sfimplf}.
 
@@
 \end{remark}
-This means that there is no `strong gluing'.
 \begin{lemma}[Practical gluing]\label{pg}
@@
     vertices, and split the graph into \emph{independent} components when
-    possible. We find an initial solution using local search that tries to move
-    slices and optimally insert them, and re-label all nodes accordingly to make
+    possible. We find an initial solution using the median heuristic \cite{eades_median,eades_median_2} and a local search that tries to move
+    slices and optimally insert them \cite{makinen_experiments,eades_heuristcis}, and re-label all nodes accordingly to make
     memory accesses more efficient.
@@
 \end{description}
+
+\bibliography{bibliography}
+
 \end{document}

### 2024-06-24 tex/description.tex
dujmovic citations

@@
 We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
-is a \emph{fixed} pair. The following result is well known \cite[Fact 4]{dujmovic_2004}.
+is a \emph{fixed} pair. The following result is well known \cite[Lemma
+  1]{dujmovic_2004}, \cite[RR1]{dujmovic_2008}.
 
@@
 We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
-generalization possible when only considering $u, v$ themselves (see \cref{rem:strongest}).
+generalization possible when only considering $u, v$ themselves (see
+\cref{rem:strongest}). This generalizes \cite[RR3]{dujmovic_2008}.
 \begin{definition}[Strongly fixed pair]
@@
 Although such a function $X$ may exist in theory, it does
-not have to exist in the actual set $B$, motivating the following definition.
+not have to exist in the actual set $B$, motivating the following definition
+that generalizes \cite[RRLO2]{dujmovic_2008}.
 
@@
 
-Let us also mention this gluing-like reduction: \emph{gluing to the front}.
+Let us also mention this gluing-like reduction: \emph{gluing to the front} \cite[RRLO1]{dujmovic_2008}
 \begin{lemma}[Greedy]\label{greedy}
@@
     possible. We find an initial solution using the median heuristic \cite{eades_median,eades_median_2} and a local search that tries to move
-    slices and optimally insert them \cite{makinen_experiments,eades_heuristcis}, and re-label all nodes accordingly to make
+    slices and optimally insert them \cite{makinen_experiments,eades_heuristics}, and re-label all nodes accordingly to make
     memory accesses more efficient.

### 2024-06-24 tex/description.tex
cleanup
citation for splitting
move zenodo DOI from related to supplement

@@
 
-\relatedversion{\url{https://doi.org/10.5281/zenodo.11671980}} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%% \relatedversion{\url{https://doi.org/10.5281/zenodo.11671980}} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
 %\relatedversiondetails[linktext={opt.
@@
 \supplementdetails[subcategory={Source Code}]{Software}{https://github.com/mjdv/ocmu64} %linktext, cite, and subcategory are optional
+\supplementdetails[subcategory={Source Code}]{Software}{https://doi.org/10.5281/zenodo.11671980} %linktext, cite, and subcategory are optional
 
@@
   \item[Graph simplification] We drop degree-$0$ vertices, merge identical
-    vertices, and split the graph into \emph{independent} components when
+    vertices, and split the graph into \emph{independent} components
+    \cite[Corollary 2]{dujmovic_2004} when
     possible. We find an initial solution using the median heuristic \cite{eades_median,eades_median_2} and a local search that tries to move
@@
 
+\newpage
+
 \bibliography{bibliography}

### 2024-06-24 tex/description.tex
Small rephrasings.

@@
 is a \emph{fixed} pair. The following result is well known \cite[Lemma
-  1]{dujmovic_2004}, \cite[RR1]{dujmovic_2008}.
+  1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.
 
@@
 generalization possible when only considering $u, v$ themselves (see
-\cref{rem:strongest}). This generalizes \cite[RR3]{dujmovic_2008}.
+\cref{rem:strongest}). This also generalizes RR3 of \cite{dujmovic_2008}.
 \begin{definition}[Strongly fixed pair]
@@
 not have to exist in the actual set $B$, motivating the following definition
-that generalizes \cite[RRLO2]{dujmovic_2008}.
+that generalizes RRLO2 of \cite{dujmovic_2008}.
 
@@
 
-Let us also mention this gluing-like reduction: \emph{gluing to the front} \cite[RRLO1]{dujmovic_2008}
+Let us also mention this gluing-like reduction: \emph{gluing to the front}, implied by RRL01 of
+\cite{dujmovic_2008}.
 \begin{lemma}[Greedy]\label{greedy}

### 2024-06-24 tex/description.tex
abstract

@@
 
-  We prove a number of novel reductions, and apply these in our solver OCMu64
-  that directly uses branch-and-bound on the ordering of the vertices of $B$ and
-  does not depend on ILP or SAT solvers.
+  We introduce the novel \emph{strongly fixed}, \emph{practically fixed}, and
+  \emph{practically glued} reductions that maximally generalize some existing
+  reductions.
+  We apply these in our exact solver OCMu64, that directly uses branch-and-bound
+  on the ordering of the vertices of $B$ and does not depend on ILP or SAT
+  solvers.
 \end{abstract}

### 2024-08-30 tex/poster.tex
poster WIP

--- 2024-06-24 tex/description.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling thm-restate support, use "thm-restate"
+% Unofficial University of Cambridge Poster Template
+% https://github.com/andiac/gemini-cam
+% a fork of https://github.com/anishathalye/gemini
+% also refer to https://github.com/k4rtik/uchicago-poster
 
-\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+\documentclass[final]{beamer}
 
-\graphicspath{{./fig/}}%helpful if your graphic files are in another directory
+% ====================
+% Packages
+% ====================
 
-\bibliographystyle{plainurl}% the mandatory bibstyle
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage[orientation=portrait,size=a2,scale=1.15]{beamerposter}
+\usetheme{gemini}
+\usecolortheme{nott}
+\usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.14}
+\usepackage{anyfontsize}
 
-\title{OCMu64: a solver for One-sided Crossing Minimization} %TODO Please add
+% ====================
+% Lengths
+% ====================
 
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
+% If you have N columns, choose \sepwidth and \colwidth such that
+% (N+1)*\sepwidth + N*\colwidth = \paperwidth
+\newlength{\sepwidth}
+\newlength{\colwidth}
+\setlength{\sepwidth}{0.025\paperwidth}
+\setlength{\colwidth}{0.45\paperwidth}
 
-\author{Ragnar {Groot Koerkamp}}{ETH Zurich, Switzerland}{ragnar.grootkoerkamp@gmail.com}{https://orcid.org/0000-0002-2091-1237}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
-Please provide at least the name of the affiliation and the country.
-The full address is optional.
-Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.
+\newcommand{\separatorcolumn}{\begin{column}{\sepwidth}\end{column}}
 
-\author{Mees de Vries}{Unaffiliated, Netherlands}{meesdevries@protonmail.com}{}{}
+% ====================
+% Title
+% ====================
 
-\authorrunning{R. Groot Koerkamp and M. de Vries} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+\title{OCMu64: a solver for One-sided Crossing Minimization}
 
-\Copyright{Ragnar Groot Koerkamp and Mees de Vries} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\author{Ragnar {Groot Koerkamp} \inst{1} \and Mees de vries \inst{2}}
 
-\ccsdesc[500]{Theory of computation~Mathematical optimization}
-\ccsdesc[300]{Theory of computation~Computational geometry}
+\institute[shortinst]{\inst{1} ETH Zurich, @curious\_coding \samelineand
+  \inst{2} Unaffiliated, The Netherlands}
 
-\keywords{Graph drawing, crossing number, branch and bound} %TODO mandatory; please add comma-separated list of keywords
+% ====================
+% Footer (optional)
+% ====================
 
-\category{} %optional, e.g. invited paper
+%% \footercontent{
+%%   \href{https://utfpr.edu.br/ct/ppgca}{utfpr.edu.br/ct/ppgca} \hfill
+%%   Mostra de Trabalhos do PPGCA --- TechTalks 2024 \hfill
+%%   \href{mailto:ppgca-ct@utfpr.edu.br}{ppgca-ct@utfpr.edu.br}}
+% (can be left out to remove footer)
 
-%% \relatedversion{\url{https://doi.org/10.5281/zenodo.11671980}} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversiondetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g.
-Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional
+% ====================
+% Logo (optional)
+% ====================
 
-\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-\supplementdetails[subcategory={Source Code}]{Software}{https://github.com/mjdv/ocmu64} %linktext, cite, and subcategory are optional
-\supplementdetails[subcategory={Source Code}]{Software}{https://doi.org/10.5281/zenodo.11671980} %linktext, cite, and subcategory are optional
+% use this to include logos on the left and/or right side of the header:
+%% \logoright{\includegraphics[height=2.5cm]{logos/utfpr-logo.png}}
+%% \logoleft{\hspace{20ex}\includegraphics[height=3.5cm]{logos/ppgca-logo.png}}
 
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
+% CUSTOM MACROS
 
-%% \acknowledgements{I want to thank \dots}%optional
-
-\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \EventEditors{John Q. Open and Joan R. Access}
-%% \EventNoEds{2}
-%% \EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-%% \EventShortTitle{CVIT 2016}
-%% \EventAcronym{CVIT}
-%% \EventYear{2016}
-%% \EventDate{December 24--27, 2016}
-%% \EventLocation{Little Whinging, United Kingdom}
-%% \EventLogo{}
-%% \SeriesVolume{42}
-%% \ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{cleveref}
+\usepackage{amsthm}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
 
@@
 
+% ====================
+% Body
+% ====================
+
 \begin{document}
 
-\maketitle
+% Refer to https://github.com/k4rtik/uchicago-poster
+% logo: https://www.cam.ac.uk/brand-resources/about-the-logo/logo-downloads
+% \addtobeamertemplate{headline}{}
+% {
+%     \begin{tikzpicture}[remember picture,overlay]
+%       \node [anchor=north west, inner sep=3cm] at ([xshift=-2.5cm,yshift=1.75cm]current page.north west)
+%       {\includegraphics[height=7cm]{logos/unott-logo.eps}};
+%     \end{tikzpicture}
+% }
 
-%TODO mandatory: add short abstract of the document
-\begin{abstract}
-  Given a bipartite graph $(A,B)$, the \emph{one-sided crossing minimization}
-  (OCM) problem is to find an ordering of the vertices of $B$ that minimizes the
-  number of edge crossings when drawn in the plane.
+  % Try also: alertblock, exampleblock
+  % \heading
 
-  We prove a number of novel reductions, and apply these in our solver OCMu64
-  that directly uses branch-and-bound on the ordering of the vertices of $B$ and
-  does not depend on ILP or SAT solvers.
-\end{abstract}
+\begin{frame}[t]
+\begin{columns}[t]
+\separatorcolumn
+\begin{column}{\colwidth}
 
-\section{Introduction}
+  \begin{alertblock}{todo}
+    increase font size? Make lemmas inside blocks, not lemmas as blocks. Figures.
+  \end{alertblock}
 
+  \begin{block}{Problem statement}
 The 2024 edition of PACE, an annual optimization challenge, considers the
@@
 
-\section{Definitions}
+\heading{Definitions}
 We use $<$ to compare vertices in $A$ in their fixed ordering. We generalize to weighted graphs
@@
   1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.
+  \end{block}
 
-% TODO: Citation
-\begin{observation}\label{lem:weak}
-  When all neighbours of $u$ come before all neighbours of $v$, then $u$ comes
-  before $v$ in any solution.
-  That is, when $\max N(u) \leq \min N(v)$ and $\bar u\neq \bar v$, then $u\b v$.
-\end{observation}
-
-\section{Methods}
-\subsection{Reductions}
-\subparagraph{Fixed pairs}
-We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
-generalization possible when only considering $u, v$ themselves (see
-\cref{rem:strongest}). This also generalizes RR3 of \cite{dujmovic_2008}.
-\begin{definition}[Strongly fixed pair]
+\begin{block}{Strongly fixed pairs}
     We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
@@
     is strict. Note that this implies $r(u, v) < 0$.
-\end{definition}
-\begin{lemma}\label{lem:sfp} When $u, v$ is a strongly fixed pair,
-    then for any $w: A\to \mathbb R^{\geq 0}$ we have 
-    \[
-        r(w, \bar v) \leq r(w, \bar u).
-    \]
-\end{lemma}
-\begin{proof}
-    Consider the least element $a_0 \in A$ such that $\bar u(a_0) \neq
-    \bar v(a_0)$. We must have $\bar u(a_0) > \bar v(a_0)$. Now consider the transformation of
-    $\bar u$ which ``moves'' $\delta := \bar u(a_0) - \bar v(a_0)$ of weight from $a_0$ to its
-    successor $a_1 \in A$, and call this transformed function $\bar u'$. Then
-    \[
-        r(w, \bar u') = r(w, \bar u) - \delta w(a_0) - \delta w(a_1) \leq r(w, \bar u).
-    \]
-    Since $\bar v$ is obtained from $\bar u$ by a sequence of such transformations,
-    the inequality follows.
-\end{proof}
-\begin{lemma}\label{lem:sfimplf}
-    If $(u, v)$ is strongly fixed, then $u \b v$.
-\end{lemma}
-\begin{proof}
-    Suppose towards a contradiction that $v < x_0 < \cdots < x_k < u$ is part of an optimal
-    solution. Write $X = \sum_i x_i$ for the combined function. Then by assumption $r(X, u)
-    \leq 0$, and therefore $r(X, v) = W_v r(X, \bar v) \leq W_v r(X, \bar u) = W_v / W_u \cdot
-    r(X, u) \leq 0$. But then $c(X, u, v) < c(X, v, u)\leq c(v, X, u)$, which
-    contradicts $(v,X,u)$ being optimal.
-\end{proof}
 
-\begin{remark}
     Consider $u \neq v$ from the original, unweighted problem, taking only values $0, 1$. Let
@@
     \rfloor}$ and at least one of the inequalities is strict, which is how we check in practice whether $u, v$ is strongly fixed.
-\end{remark}
 
-\begin{remark}\label{rem:strongest}
+    \textbf{Main lemma:}
+    If $(u, v)$ is strongly fixed, then $u \b v$.
+
+    \textbf{The lamma is optimal:}
     Suppose that $u, v \in B$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in
@@
     R^{\geq 0}$ some function which assigns very high
-    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
-    \cref{lem:sfp} is optimal.
-\end{remark}
+    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$.
+\end{block}
+
+  \begin{block}{Practically fixed pairs}
 Although such a function $X$ may exist in theory, it does
@@
 
-\begin{lemma}\label{pfp}
+\textbf{Blocking set:}
   Suppose $r(u,v)< 0$.
@@
     \emph{practically fixed pair}, and $u\b v$.
-\end{lemma}
+  \end{block}
 
-In practice, such a set $X$ can be found, if one exists, using a knapsack-like algorithm: for
+  \textbf{Finding blocking sets:}
+Such a set $X$ can be found, if one exists, using a knapsack-like algorithm: for
 each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a subset summing
@@
 
-\begin{remark}[Weak variants]
-  It is also possible to consider \emph{weak} variants of the above lemmas that
-  only imply that $u < v$ in \emph{some} optimal solution. This requires careful
-  handling of cycles like $u\be v\be w\be u$.
-\end{remark}
+%% \begin{block}{Weak variants}
+%%   It is also possible to consider \emph{weak} variants of the above lemmas that
+%%   only imply that $u < v$ in \emph{some} optimal solution. This requires careful
+%%   handling of cycles like $u\be v\be w\be u$.
+%% \end{block}
 
-\subparagraph{Gluing}
+\end{column}
+
+\separatorcolumn
+
+\begin{column}{\colwidth}
+\begin{block}{Gluing}
 We now turn our attention to \emph{gluing}, i.e., proving that two vertices $u$
@@
 
-\begin{remark}
+\textbf{Remark:}
   When $N(u)=N(v)$ in the unweighted case, or more generally $\bar u=\bar v$, we can glue $u$
@@
   strictly better than $(u,v,X)$ and $(X,u,v)$.
-\end{remark}
-\begin{lemma}[Practical gluing]\label{pg}
+
+\textbf{Practical gluing lemma:}
     Let $u$ and $v$ satisfy $r(u, v) \leq 0$.
@@
     \min(c(u, v, X), c(X, u, v))$. If there is no blocking set, then we can glue $u, v$.
-\end{lemma}
+
 Again such sets $X$ can be found or proven to not exist using a knapsack
@@
 
-Let us also mention this gluing-like reduction: \emph{gluing to the front}, implied by RRL01 of
-\cite{dujmovic_2008}.
-\begin{lemma}[Greedy]\label{greedy}
+\textbf{Greedy gluing}
   When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
   starts with $u$.
-\end{lemma}
+\end{block}
 
-\begin{remark}[Tail variants]
-  Our branch-and-bound method fixes vertices of the
-solution from left to right. Thus, at each step \cref{pg,pfp} can be applied to
-just the \emph{tail}.
-\end{remark}
+  \begin{block}{Solver}
 
-\subsection{Branch-and-bound}
 Our solver \texttt{OCMu64} is based on a standard branch-and-bound on the ordering of the
@@
 \end{description}
+  \end{block}
 
-\newpage
+  \begin{block}{Performance}
+    \
+  \end{block}
 
-\bibliography{bibliography}
+  %% \begin{block}{References (optional)}
+  %%   \nocite{*}
+  %%   \footnotesize{\bibliographystyle{plain}\bibliography{poster}}
+  %% \end{block}
+
+\end{column}
+\separatorcolumn
+\end{columns}
+\end{frame}
 

### 2024-09-01 tex/poster.tex
simplify

@@
 
-\title{OCMu64: a solver for One-sided Crossing Minimization}
+\title{PACE 2024: OCMu64, reductions and a branch-and-bound solver for\\ One-sided Crossing Minimization}
 
@@
 
+\newcommand{\mees}[1]{{\color{blue}[{\bf{Bryce:}} #1]}}
+\newcommand{\ragnar}[1]{{\color{orange}[{\bf{Ragnar:}} #1]}}
+
 % ====================
@@
       \begin{alertblock}{todo}
-    increase font size? Make lemmas inside blocks, not lemmas as blocks. Figures.
+        Figures.
       \end{alertblock}
 
-  \begin{block}{Problem statement}
-The 2024 edition of PACE, an annual optimization challenge, considers the
-\emph{one-sided crossing minimization} problem, defined as follows.
+      \begin{block}{One-sided crossing minimizations}
         Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
-$(i, 1)$ and $(j,0)$ for components $A$ and $B$ respectively. The ordering of $A$
-is fixed, and the goal is the find an ordering of $B$ that minimizes the number of
+        $(i, 0)$ and $(j,1)$ for components $A$ and $B$ respectively. The ordering of $A$
+        is fixed. The goal is the find an ordering of $B$ that minimizes the number of
         crossings when edges are drawn as straight lines.
 
-We introduce some new reductions and give an overview of our algorithm. Proofs are brief or
-omitted due to lack of space.
+        \heading{Definitions}
+        We use $<$ to compare vertices in $A$ in their fixed ordering.
 
-\heading{Definitions}
-We use $<$ to compare vertices in $A$ in their fixed ordering. We generalize to weighted graphs
-for the proof of \cref{lem:sfp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
-R^{\geq 0}$, where weight 0 represents an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for
-the total weight of $u$, and set $\bar u = u/W_u$. Write $N(u) = \supp(u) \subseteq A$ for the
-set of neighbors of $u$.
+        For $u\in B$, we write $N(u) \subseteq A$ for the set of its neighbours.
 
-We write $c(u, v) = \sum_{(a, b) \in A^2}
-u(a)v(b)[a > b]$; in the unweighted case, this is the \emph{crossing number}, the number of
+        The \textbf{crossing number} $c(u, v)$ is $\sum_{(a, b) \in A^2}
+        u(a)v(b)[a > b]$, the number of
         crossings between edges incident to $u$ and $v$ when $u$ is drawn before $v$.  For
@@
 
-We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
-is a \emph{fixed} pair. The following result is well known \cite[Lemma
-  1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.
+        We write $u\b v$ when $u$ must come before $v$ in \emph{all} minimal solutions, and say that $(u, v)$
+        is a \textbf{fixed pair}.
+
+        A well known result is that when all neighbours of $u$ come before all
+        neighbours of $v$, then $u\b v$.
+
+        We try to fix as many pairs as possible to speed up the search.
       \end{block}
@@
       \begin{block}{Strongly fixed pairs}
-    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
-    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
-    is strict. Note that this implies $r(u, v) < 0$.
+        We call $u, v \in B$ a \textbf{strongly fixed pair} if their degrees are $n$
+        and $m$ and for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
+          \rfloor}$.
+        Intuitively, when \emph{the $x\%$'th neighbour of $u$ is left of the $x\%$'th
+        neighbour of $v$}. Additionally, at least one of these inequalities must be strict.
+        Note that this implies $r(u, v) < 0$.
 
-    Consider $u \neq v$ from the original, unweighted problem, taking only values $0, 1$. Let
-    $n = |N(u)|, m = |N(v)|$, and consider both as ordered lists. Then $u, v$ are strongly
-    fixed if and only if for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
-    \rfloor}$ and at least one of the inequalities is strict, which is how we check in practice whether $u, v$ is strongly fixed.
-
-    \textbf{Main lemma:}
+        \textbf{Main result:}
         If $(u, v)$ is strongly fixed, then $u \b v$.
@@
         \textbf{The lamma is optimal:}
-    Suppose that $u, v \in B$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in
-    A$ be some element such
-    that $\sum_{a \leq b} \bar u(a) > \sum_{a \leq b} \bar v(a)$. By taking $X: A \to \mathbb
-    R^{\geq 0}$ some function which assigns very high
-    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$.
+        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
+        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
+        Assuming there exists vertices $m$ in between $a$ and $b$, $l$ left of $\min
+        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
+          need reversing? Or should we just say left of the min and right of the max
+          of the two?}, there exists some \emph{weighted} distribution $X$ over
+        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
+        $v$ may have to go before $u$.
       \end{block}
@@
         Although such a function $X$ may exist in theory, it does
-not have to exist in the actual set $B$, motivating the following definition
-that generalizes RRLO2 of \cite{dujmovic_2008}.
+        not have to exist in the actual set $B$, motivating a more practical approach:
 
         \textbf{Blocking set:}
-  Suppose $r(u,v)< 0$.
+        Suppose $r(u,v)< 0$, i.e., $u$ wants to go left of $v$.
         A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) \leq \min(c(v, u,
@@
 
-Note that we do not require $(v, X, u)$ to be a true local minimum, since we do
-not consider interactions between vertices in $X$, as that would make ruling out the
-existence of such sets much harder.
+      %% Note that we do not require $(v, X, u)$ to be a true local minimum, since we do
+      %% not consider interactions between vertices in $X$, as that would make ruling out the
+      %% existence of such sets much harder.
 
@@
       \begin{block}{Gluing}
-We now turn our attention to \emph{gluing}, i.e., proving that two vertices $u$
-and $v$ always go right next to each other, and we can treat them as a single vertex. First,
-let us see that we cannot get `strong gluing' result analogous to \cref{lem:sfimplf}.
+        A second reduction strategy \emph{glues} vertices $u$ and $v$ together.
+        I.e., when $u$ and $v$ are consucutive in \emph{all} optimal solutions,
+        we \textbf{glue} them together and treat them as a single vertex.
 
-\textbf{Remark:}
-  When $N(u)=N(v)$ in the unweighted case, or more generally $\bar u=\bar v$, we can glue $u$
-    and $v$.
-  Otherwise when $r(u,v)\leq 0$, there is an $X : A\to \mathbb R^{\geq 0}$ such that $(u, X, v)$ is
-  strictly better than $(u,v,X)$ and $(X,u,v)$.
+        \textbf{Gluing identical nodes:}
+        When $u$ and $v$ have the same neighbours, we can glue $u$ and $v$.
 
-\textbf{Practical gluing lemma:}
+        \textbf{Greedy gluing:}
+        When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
+        starts with $u$.
+
+        \textbf{Practical gluing lemma (unused):}
         Let $u$ and $v$ satisfy $r(u, v) \leq 0$.
@@
         set summing to $\leq{}(0,0)$.
-
-\textbf{Greedy gluing}
-  When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
-  starts with $u$.
       \end{block}
@@
       \begin{block}{Solver}
-
-Our solver \texttt{OCMu64} is based on a standard branch-and-bound on the ordering of the
-solution.  We start with fixed prefix $P=()$ and tail $T=B$, and in each step we try (a
+        Our solver \texttt{OCMu64} uses a standard \textbf{branch-and-bound on the ordering of the
+        solution}.  We start with fixed prefix $P=()$ and tail $T=B$, and in each step we try (a
         subset of) all vertices in $T$ as the next vertex appended to $P$.
@@
         \sum_{u,v}\min(c(u,v),c(v,u))$ on the score.
-We keep track of the score $S_P$ of the prefix and $S_{PT}=c(P, T)$ of
-prefix-tail intersections, and abort when this score goes above the best
-solution found so far. The \emph{excess} of a tail is its optimal score minus
-the trivial lower bound. We do a number of optimizations.
+        %% We keep track of the score $S_P$ of the prefix and $S_{PT}=c(P, T)$ of
+        %% prefix-tail intersections, and abort when this score goes above the best
+        %% solution found so far.
 
@@
         \item[Graph simplification] We drop degree-$0$ vertices, merge identical
-    vertices, and split the graph into \emph{independent} components
-    \cite[Corollary 2]{dujmovic_2004} when
-    possible. We find an initial solution using the median heuristic \cite{eades_median,eades_median_2} and a local search that tries to move
-    slices and optimally insert them \cite{makinen_experiments,eades_heuristics}, and re-label all nodes accordingly to make
+          vertices, and split the graph into \emph{independent} components.
+          The initial solution uses the median heuristic and a local search that tries to move
+          slices and optimally insert them. We then re-label all nodes in order to make
           memory accesses more efficient.
         \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
-    exact track we also find practically fixed pairs. Instances for the parameterized
-    track are simple enough that the overhead was not worth it. Also for each
-    tail we search for new `tail-local' practically fixed pairs. In each state, we only
+          exact track we also find practically fixed pairs.
+          For each tail we search for \emph{tail-local} practically fixed pairs. In each state, we only
           try vertices $u\in T$ not fixed by another $v\in T$.
-  \item[Gluing] We use the greedy strategy of \cref{greedy}. Our implementation
-    of \cref{pg} contained a bug, so we did not use this. (Also benefits
-    seemed limited.)
+        \item[Gluing] We use the greedy gluing strategy. Our implementation
+          of practical gluing contained a bug, so we did not use this.
         \item[Tail cache] In each step, we search for the longest suffix of $T$ that
-    was seen before, and reuse (the lower bound on) its excess. We also
+          was seen before, and reuse (the lower bound on) its score. We also
           cache the tail-local practically fixed pairs.
         \item[Optimal insert] Instead of simply appending $u$ to $P$, we
-    insert it in the optimal position. Note that the
+          insert it in the optimal position. The
           implementation is tricky because it interacts in complicated ways with
@@
       \begin{block}{Performance}
-    \
+
       \end{block}

### 2024-09-01 tex/poster.tex
perf
Insert figures

@@
 
-      \begin{alertblock}{todo}
-        Figures.
-      \end{alertblock}
-
       \begin{block}{One-sided crossing minimizations}
@@
 
-        \heading{Definitions}
         We use $<$ to compare vertices in $A$ in their fixed ordering.
-
         For $u\in B$, we write $N(u) \subseteq A$ for the set of its neighbours.
@@
         is a \textbf{fixed pair}.
+        We try to fix as many pairs as possible to speed up the search.
+        A well known result is that when $\max N(u) < \min N(v)$, then $u\b v$.
 
-        A well known result is that when all neighbours of $u$ come before all
-        neighbours of $v$, then $u\b v$.
-
-        We try to fix as many pairs as possible to speed up the search.
+        \vspace{-1em}
+        \centering
+        \includegraphics[scale=2]{fig/simple.pdf}
       \end{block}
@@
         $v$ may have to go before $u$.
+
+        \centering
+        \includegraphics[scale=1.5]{fig/strongly-fixed.pdf}
+
       \end{block}
@@
 
+        \centering
+        \includegraphics[scale=2]{fig/blocking-set.pdf}
     \end{column}
@@
         When $u$ and $v$ have the same neighbours, we can glue $u$ and $v$.
+
+        \begin{center}
+          \vspace{-2em}
+        \includegraphics[scale=2]{fig/gluing.pdf}
+        \end{center}
 
@@
       \begin{block}{Performance}
+        \textbf{Parameterized track:} All 200 instances in \textbf{10.37s} total
+        time (second place).
+
+        \textbf{Exact track:} 157/200 instanes.
 

### 2024-09-03 tex/poster.tex
Fix small typos.

@@
 
-        \textbf{The lamma is optimal:}
+        \textbf{The lemma is optimal:}
         Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
         such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
-        Assuming there exists vertices $m$ in between $a$ and $b$, $l$ left of $\min
+        Assuming there exist vertices $m$ in between $a$ and $b$, $l$ left of $\min
         N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$

### 2024-09-03 tex/poster.tex
Change Strongly Fixed Pairs paragraph

@@
         \textbf{The lemma is optimal:}
+        Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
+          possible to prove $u \b v$ if $(u, v)$ is not strongly fixed.
         Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
-        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
-        Assuming there exist vertices $m$ in between $a$ and $b$, $l$ left of $\min
-        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
-          need reversing? Or should we just say left of the min and right of the max
-          of the two?}, there exists some \emph{weighted} distribution $X$ over
-        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
-        $v$ may have to go before $u$.
+        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
+          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with $R > \max(N(u))$.
+          Add a node $X \in B$ connected to $L, M, R$. With the correct numbers of vertices in
+          $L, M, $ we can make it so that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
+        $v$ has to go before $u$.
 
@@
       \begin{block}{Practically fixed pairs}
-        Although such a function $X$ may exist in theory, it does
+        Although such a node $X$ may exist in theory, it does
         not have to exist in the actual set $B$, motivating a more practical approach:

### 2024-09-03 tex/poster.tex
s/X/x

@@
           R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with $R > \max(N(u))$.
-          Add a node $X \in B$ connected to $L, M, R$. With the correct numbers of vertices in
-          $L, M, $ we can make it so that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
+          Add a node $x \in B$ connected to $L, M, R$. With the correct numbers of vertices in
+          $L, M, $ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
         $v$ has to go before $u$.
@@
       \begin{block}{Practically fixed pairs}
-        Although such a node $X$ may exist in theory, it does
+        Although such a node $x$ may exist in theory, it does
         not have to exist in the actual set $B$, motivating a more practical approach:

### 2024-09-03 tex/poster.tex
Add missing R back in

@@
           Add a node $x \in B$ connected to $L, M, R$. With the correct numbers of vertices in
-          $L, M, $ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
+          $L, M, R$ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
         $v$ has to go before $u$.

### 2024-09-03 tex/poster.tex
various changes

--- 2024-09-03 tex/poster.tex
@@
 
-      \begin{block}{One-sided crossing minimizations}
+      \begin{block}{One-sided crossing minimization}
         Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
@@
 
-        \vspace{-1em}
+        \vspace{-1.5em}
         \centering
@@
       \begin{block}{Strongly fixed pairs}
-        We call $u, v \in B$ a \textbf{strongly fixed pair} if their degrees are $n$
-        and $m$ and for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
-          \rfloor}$.
-        Intuitively, when \emph{the $x\%$'th neighbour of $u$ is left of the $x\%$'th
-        neighbour of $v$}. Additionally, at least one of these inequalities must be strict.
-        Note that this implies $r(u, v) < 0$.
+        We call $u, v \in B$ a \textbf{strongly fixed pair} if $N(u) \neq N(v)$
+        and their degrees are $n$
+        and $m$ and for all $0 \leq i < n$,
+        $$N(u)_i \leq N(v)_{\lfloor i\cdot m/n \rfloor}.$$
+        That is: for all $x$, \emph{the $x\%$'th neighbour of $u$ is left of the $x\%$'th
+        neighbour of $v$}.
+        %% Note that this implies $r(u, v) < 0$.
+
+        \begin{center}
+          \vspace{-2em}
+        \includegraphics[scale=1.5]{fig/strongly-fixed.pdf}
+          \vspace{-2em}
+        \end{center}
 
@@
         such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
-          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with $R > \max(N(u))$.
-          Add a node $x \in B$ connected to $L, M, R$. With the correct numbers of vertices in
-          $L, M, $ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
+          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with
+          $\max(N(u)) < R$.
+          Add a node $x \in B$ connected to $L$, $M$, $R$. With the correct numbers of vertices in
+          $L$, $M$, $R$ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
         $v$ has to go before $u$.
@@
         \centering
-        \includegraphics[scale=1.5]{fig/strongly-fixed.pdf}
+          \vspace{-0.5em}
+        \includegraphics[scale=2]{fig/blocking-set.pdf}
+          \vspace{-1em}
 
@@
       %% \end{block}
-
-        \centering
-        \includegraphics[scale=2]{fig/blocking-set.pdf}
     \end{column}
@@
       \begin{block}{Gluing}
-        A second reduction strategy \emph{glues} vertices $u$ and $v$ together.
-        I.e., when $u$ and $v$ are consucutive in \emph{all} optimal solutions,
+        When $u$ and $v$ are consecutive in \emph{all} optimal solutions,
         we \textbf{glue} them together and treat them as a single vertex.
 
-        \textbf{Gluing identical nodes:}
-        When $u$ and $v$ have the same neighbours, we can glue $u$ and $v$.
+        \textbf{Identical nodes:}
+        When $u$ and $v$ have the same neighbours, we glue them.
 
         \begin{center}
-          \vspace{-2em}
+          \vspace{-1em}
         \includegraphics[scale=2]{fig/gluing.pdf}
@@
 
+        \ragnar{A figure of prefix and tail and optimal insert here would be
+          nice to make the section less boring.}
+
         \begin{description}
-        \item[Graph simplification] We drop degree-$0$ vertices, merge identical
-          vertices, and split the graph into \emph{independent} components.
-          The initial solution uses the median heuristic and a local search that tries to move
-          slices and optimally insert them. We then re-label all nodes in order to make
-          memory accesses more efficient.
+        \item[Graph simplification]
+          %% We drop degree-$0$ vertices, merge identical
+          %% vertices, and split the graph into \emph{independent} components.
+          The initial solution uses the median heuristic followed by a simple local search that tries to move
+          slices and optimally insert them.
+          We then re-label all nodes in order to make memory accesses more efficient.
         \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
@@
           For each tail we search for \emph{tail-local} practically fixed pairs. In each state, we only
-          try vertices $u\in T$ not fixed by another $v\in T$.
-        \item[Gluing] We use the greedy gluing strategy. Our implementation
+          try vertices $u\in T$ not fixed after another $v\in T$.
+        \item[Gluing\quad] We use the greedy gluing strategy. Our implementation
           of practical gluing contained a bug, so we did not use this.

### 2024-09-03 tex/poster.tex
drop comment
shrink fig
fix too small text
Fix name typo, lemma -> result

@@
 
-\author{Ragnar {Groot Koerkamp} \inst{1} \and Mees de vries \inst{2}}
+\author{Ragnar {Groot Koerkamp} \inst{1} \and Mees de Vries \inst{2}}
 
@@
 
-        \textbf{The lemma is optimal:}
+        \textbf{This result is optimal:}
         Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
@@
           \vspace{-0.5em}
-        \includegraphics[scale=2]{fig/blocking-set.pdf}
+        \includegraphics[scale=1.5]{fig/blocking-set.pdf}
           \vspace{-1em}
-
       \end{block}
@@
         \emph{practically fixed pair}, and $u\b v$.
-      \end{block}
 
@@
         to ${\leq{}(r(u, v), r(u, v))}$.
+
+      \end{block}
 
@@
 
-        \ragnar{A figure of prefix and tail and optimal insert here would be
-          nice to make the section less boring.}
-
         \begin{description}

### 2024-09-20 tex/paper.tex
Fix remark 6, add proof, needs simplification

--- 2024-06-24 tex/description.tex
@@
 
-\author{Mees de Vries}{Unaffiliated, Netherlands}{meesdevries@protonmail.com}{}{}
+\author{Mees de Vries}{Unaffiliated, The Netherlands}{meesdevries@protonmail.com}{}{}
 
@@
 We write $u\b v$ when $u$ must come before $v$ in all minimal solutions, and say that $(u, v)$
-is a \emph{fixed} pair. The following result is well known \cite[Lemma
+is a \emph{fixed} pair.
+
+\section{Methods}
+\subsection{Reductions}
+\subparagraph{Fixed pairs}
+To reduce the search space of all possible orderings of $B$, it is crucial to automatically
+find as many fixed pairs in $B$ as possible. Ideally, one would be able to determine whether $u
+\b v$ by inspecting only $u, v$. For example, the following result is well known \cite[Lemma
   1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.
@@
 \begin{observation}\label{lem:weak}
-  When all neighbours of $u$ come before all neighbours of $v$, then $u$ comes
-  before $v$ in any solution.
-  That is, when $\max N(u) \leq \min N(v)$ and $\bar u\neq \bar v$, then $u\b v$.
+  Let $u, v \in B$. When $\max N(u) \leq \min N(v)$ and $\bar u\neq \bar v$, then $u\b v$.
 \end{observation}
 
-\section{Methods}
-\subsection{Reductions}
-\subparagraph{Fixed pairs}
 We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
-generalization possible when only considering $u, v$ themselves (see
-\cref{rem:strongest}). This also generalizes RR3 of \cite{dujmovic_2008}.
+generalization possible when only considering $u, v$ themselves, without further inspection of
+$A$ or the other elements of $B$ (see \cref{rem:strongest}). This also generalizes RR3 of
+\cite{dujmovic_2008}.
+
 \begin{definition}[Strongly fixed pair]
@@
     fixed if and only if for all $0 \leq i < n$, $N(u)_i \leq N(v)_{\lfloor i\cdot m/n
-    \rfloor}$ and at least one of the inequalities is strict, which is how we check in practice whether $u, v$ is strongly fixed.
+    \rfloor}$ and at least one of the inequalities is strict, which is how we check in practice
+    whether $u, v$ is strongly fixed.
 \end{remark}
@@
 \begin{remark}\label{rem:strongest}
+    By inspecting only $u, v$, it is not possible to do better than \cref{lem:sfimplf}. If $u,
+    v$ with $\bar u \neq \bar v$ are not strongly fixed, and we can assume the existence of any
+    additional nodes in $A, B$, then we can conjure a situation where $v \b u$.
+
+    Suppose that $b \in A$ be some element such that $U := \sum_{a \leq b} \bar u(a) < \sum_{a \leq
+    b} \bar v(a) =: V$, and take $M \in A$ to be some element between $b$ and its succesor. Also,
+    take $L < \min(N(v))$ and $R > \max(N(u))$. Now consider a new element $X \in B$, which
+    connects only to $L, M, R$. We claim that by picking the right weights for $X$, we can
+    obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, which establishes that in the presence
+    of $X$, $v \b u$.
+
+    We have that
+    \[
+        c(X, u, v) - c(v, X, u) = r(u, v) + W_v(2VX(M) + X(R) - X(L) - X(M))
+    \]
+    and
+    \[
+        c(u, v, X) - c(v, X, u) = r(u, v) + W_u(X(L) + (1-U)X(M) - X(R) - UX(M)),
+    \]
+    and if we can choose $X(L), X(M), X(R)$ so that both these values are positive, we are
+    done. We can always scale these values up, so we can ignore the $r(u, v)$ term in both
+    equations; we can also ignore $W_u, W_v$. Because we can choose $X(R), X(L)$ as we please,
+    it suffices if the sum of the remaining pairs of expressions, which is
+    \[
+        (2V - 1)X(M) - (2U - 1)X(M),
+    \]
+    is positive. But indeed it is, since by assumption $U < V$.
+
     Suppose that $u, v \in B$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in

### 2024-09-20 tex/paper.tex
figures
reference figures

@@
 
+\begin{figure}[t]
+\centering
+\hfill
+\subfloat[An instance of \cref{lem:weak}.]{
+\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
+\label{fig:simple}
+}
+\hfill
+\subfloat[Examples of blocking sets in blue.]{
+\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
+\label{fig:blocking-set}
+}
+\hfill
+\\
+\subfloat[Examples of strongly fixed pairs.]{
+\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
+\label{fig:strongly-fixed}
+}
+%% \subfloat[]{
+%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
+%% \label{fig:gluing}
+%% }
+\caption{
+  Various examples where $u\b v$, where $u,v\in B$ can freely move around and
+  their neighbours in $A$ (on the dashed line) have fixed positions.}%
+\label{fig}
+\end{figure}
+
 \section{Methods}
@@
 find as many fixed pairs in $B$ as possible. Ideally, one would be able to determine whether $u
-\b v$ by inspecting only $u, v$. For example, the following result is well known \cite[Lemma
+\b v$ by inspecting only $u, v$. For example, the following result, shown in \cref{fig:simple} is well known \cite[Lemma
   1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.
@@
 
-We give a much stronger version of \cref{lem:weak}. In fact, \cref{lem:sfp} is the strongest
-generalization possible when only considering $u, v$ themselves, without further inspection of
+We give a much stronger version of \cref{lem:weak}, with some examples in \cref{fig:strongly-fixed}. In fact, \cref{lem:sfp} is the strongest
+generalization possible when only considering $u$ and $v$ themselves, without further inspection of
 $A$ or the other elements of $B$ (see \cref{rem:strongest}). This also generalizes RR3 of
@@
 
-In practice, such a set $X$ can be found, if one exists, using a knapsack-like algorithm: for
+In practice, such a blocking set $X$ can be found, if one exists, using a knapsack-like algorithm: for
 each $x\in B-\{u,v\}$, add a point $P_x = (r(v, x), r(x, u))$, and search for a subset summing
-to ${\leq{}(r(u, v), r(u, v))}$.
+to ${\leq{}(r(u, v), r(u, v))}$. \cref{fig:blocking} shows some examples.
 

### 2024-09-20 tex/paper.tex
update title
Reference lemma/observation in figure caption

@@
 
-\title{OCMu64: a solver for One-sided Crossing Minimization} %TODO Please add
+\title{PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization} %TODO Please add
 
@@
 \hfill
-\subfloat[Examples of blocking sets in blue.]{
+\subfloat[Examples of blocking sets (\cref{pfp}) in blue.]{
 \includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
-\label{fig:blocking-set}
+\label{fig:blocking}
 }
@@
 \\
-\subfloat[Examples of strongly fixed pairs.]{
+\subfloat[Examples of strongly fixed pairs (\cref{def:sfp}).]{
 \includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
@@
 
-\begin{definition}[Strongly fixed pair]
+\begin{definition}[Strongly fixed pair]\label{def:sfp}
     We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a

### 2024-09-20 tex/paper.tex
more fig caption

@@
 \hfill
-\subfloat[Examples of blocking sets (\cref{pfp}) in blue.]{
+\subfloat[Examples of blocking sets (\cref{pfp}), preventing $u\b v$.]{
 \includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
@@
 \caption{
-  Various examples where $u\b v$, where $u,v\in B$ can freely move around and
+  Various examples where $u$ must come before $v$ ($u\b v$), where $u,v\in B$ can freely move around and
   their neighbours in $A$ (on the dashed line) have fixed positions.}%

### 2024-09-20 tex/paper.tex
Revised remark 6

@@
 for the proof of \cref{lem:sfp}: a node $u \in B$ is taken to be a function $u: A \to \mathbb
-R^{\geq 0}$, where weight 0 represents an absent edge. We write $W_u = \sum_{a \in A}u(a)$ for
-the total weight of $u$, and set $\bar u = u/W_u$. Write $N(u) = \supp(u) \subseteq A$ for the
-set of neighbors of $u$.
+R^{\geq 0}$, where weight 0 represents an absent edge. Write $N(u) = \supp(u) \subseteq A$ for the
+set of neighbors of $u$. We write $W_u = \sum_{a \in A}u(a)$ for the total weight of $u$, and
+set $\bar u = u/W_u$. We think of $\bar u$ as a probability distribution, and also consider the
+cumulative distribution function $F_{\bar u}(b) = \sum_{a \leq b} \bar u(a)$.
 
@@
 
-\begin{definition}[Strongly fixed pair]\label{def:sfp}
-    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have ${\sum_{a
-    \leq b} \bar u(a) \geq \sum_{a \leq b} \bar v(a)}$, and at least one of these inequalities
+\begin{definition}[Strongly fixed pair]
+    We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have $F_{\bar
+    u}(b) \geq F_{\bar v}(b)$, and at least one of these inequalities
     is strict. Note that this implies $r(u, v) < 0$.
@@
 \begin{remark}\label{rem:strongest}
-    By inspecting only $u, v$, it is not possible to do better than \cref{lem:sfimplf}. If $u,
-    v$ with $\bar u \neq \bar v$ are not strongly fixed, and we can assume the existence of any
-    additional nodes in $A, B$, then we can conjure a situation where $v \b u$.
+    Suppose that $u, v$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in A$ be
+    such that $F_{\bar u}(b) < F_{\bar v}(b)$. Furthermore suppose that there are nodes $l, m,
+    r \in A$, with $m$ sitting between $b$ and its successor in $A$, and $l < (\supp(u) \cup
+    \supp(v)) < r$. Then consider a node $X \in B$ which is connected to $l, m, r$. By choosing
+    the weights of $X$ appropriately, we can let both $r(X, v) = W_v r(X, \bar v)$ and $r(u, X)
+    = W_u r(\bar u, X)$ grow arbitrarily large. Since we can scale up the weights of $X$, it
+    suffices to make $r(X, \bar v)$ and $r(\bar u, X)$ simultaneously positive.
 
-    Suppose that $b \in A$ be some element such that $U := \sum_{a \leq b} \bar u(a) < \sum_{a \leq
-    b} \bar v(a) =: V$, and take $M \in A$ to be some element between $b$ and its succesor. Also,
-    take $L < \min(N(v))$ and $R > \max(N(u))$. Now consider a new element $X \in B$, which
-    connects only to $L, M, R$. We claim that by picking the right weights for $X$, we can
-    obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, which establishes that in the presence
-    of $X$, $v \b u$.
-
-    We have that
+    Now $r(X, \bar v) = (2F_{\bar v}(b) - 1)X(m) + (X(r) - X(l))$, and $r(\bar u, X) = (1 -
+    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing $X(r), X(l)$ appropriately, we can make
+    these two values equal, so it suffices if their \emph{average} is positive; and indeed 
     \[
-        c(X, u, v) - c(v, X, u) = r(u, v) + W_v(2VX(M) + X(R) - X(L) - X(M))
+        (r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0.
     \]
-    and
-    \[
-        c(u, v, X) - c(v, X, u) = r(u, v) + W_u(X(L) + (1-U)X(M) - X(R) - UX(M)),
-    \]
-    and if we can choose $X(L), X(M), X(R)$ so that both these values are positive, we are
-    done. We can always scale these values up, so we can ignore the $r(u, v)$ term in both
-    equations; we can also ignore $W_u, W_v$. Because we can choose $X(R), X(L)$ as we please,
-    it suffices if the sum of the remaining pairs of expressions, which is
-    \[
-        (2V - 1)X(M) - (2U - 1)X(M),
-    \]
-    is positive. But indeed it is, since by assumption $U < V$.
-
-    Suppose that $u, v \in B$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in
-    A$ be some element such
-    that $\sum_{a \leq b} \bar u(a) > \sum_{a \leq b} \bar v(a)$. By taking $X: A \to \mathbb
-    R^{\geq 0}$ some function which assigns very high
-    weight to $b$, we can obtain $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, showing that
-    \cref{lem:sfp} is optimal.
+    Therefore, the right choice of weights of $X$ creates a situation where $c(v, X, u) <
+    \min(c(X, u, v), c(u, v, X))$. This demonstrates that if you want to show $u \b v$, and $u,
+    v$ are not strongly fixed, you must consider other features of the graph than $u, v$ and
+    their weights: \cref{lem:sfp} is optimal. Note: this also applies in the unweighted case,
+    by taking $l, m, r$ to be sets of nodes rather than single nodes.
 \end{remark}
-Although such a function $X$ may exist in theory, it does
+Although such a node $X$ may exist in theory, it does
 not have to exist in the actual set $B$, motivating the following definition

### 2024-09-20 tex/paper.tex
shrink to 4 pages

@@
 
-Let us also mention this gluing-like reduction: \emph{gluing to the front}, implied by RRL01 of
-\cite{dujmovic_2008}.
+Let us also mention this gluing-like reduction: \emph{gluing to the front}, implied by
+\cite[RRL01]{dujmovic_2008}.
 \begin{lemma}[Greedy]\label{greedy}
-  When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
-  starts with $u$.
+  \!\!When $r(u, x)\leq 0$ for all $x\in B$, there is a solution that
+  starts with $u$.\!\!
 \end{lemma}
@@
 
-\newpage
-
 \bibliography{bibliography}

### 2024-09-20 tex/paper.tex
remark 6 slight rephrasing; state the 'goal' early

@@
     Suppose that $u, v$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in A$ be
-    such that $F_{\bar u}(b) < F_{\bar v}(b)$. Furthermore suppose that there are nodes $l, m,
+    such that $F_{\bar u}(b) < F_{\bar v}(b)$.
+    We would like to construct a node $X\in B$ such that $c(v, X, u) < \min(c(X,
+    u, v), c(u, v, X))$, so that $v\b u$.
+    Suppose that there are nodes $l, m,
     r \in A$, with $m$ sitting between $b$ and its successor in $A$, and $l < (\supp(u) \cup
-    \supp(v)) < r$. Then consider a node $X \in B$ which is connected to $l, m, r$. By choosing
+    \supp(v)) < r$. Then let $X$ be connected to $l, m, r$. By choosing
     the weights of $X$ appropriately, we can let both $r(X, v) = W_v r(X, \bar v)$ and $r(u, X)
@@
     Now $r(X, \bar v) = (2F_{\bar v}(b) - 1)X(m) + (X(r) - X(l))$, and $r(\bar u, X) = (1 -
-    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing $X(r), X(l)$ appropriately, we can make
-    these two values equal, so it suffices if their \emph{average} is positive; and indeed 
-    \[
-        (r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0.
-    \]
-    Therefore, the right choice of weights of $X$ creates a situation where $c(v, X, u) <
-    \min(c(X, u, v), c(u, v, X))$. This demonstrates that if you want to show $u \b v$, and $u,
-    v$ are not strongly fixed, you must consider other features of the graph than $u, v$ and
-    their weights: \cref{lem:sfp} is optimal. Note: this also applies in the unweighted case,
-    by taking $l, m, r$ to be sets of nodes rather than single nodes.
+    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing the weights $X(r), X(l)$ appropriately, we can make
+    these two values equal, so it suffices if their \emph{average} is positive, and indeed
+    $${(r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0}.$$
+    This implies $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, and thus
+    demonstrates that if one wants to show that $u \b v$, when $u,
+    v$ are not strongly fixed, one must consider features of the graph other than $u, v$ and
+    their neighbours, so indeed \cref{lem:sfp} is optimal. Note that this also applies in the unweighted case,
+    by taking $l, m, r$ to be sets of nodes rather than weighted single nodes.
 \end{remark}
+
 Although such a node $X$ may exist in theory, it does

### 2024-09-20 tex/paper.tex
add some citations for the trivial lower bound

@@
 \b v$ by inspecting only $u, v$. For example, the following result, shown in \cref{fig:simple} is well known \cite[Lemma
-  1]{dujmovic_2004}, RR1 of \cite{dujmovic_2008}.
+  1]{dujmovic_2004}, \cite[RR1]{dujmovic_2008}.
 
@@
 
-\begin{definition}[Strongly fixed pair]
+\begin{definition}[Strongly fixed pair]\label{def:sfp}
     We call $u, v \in B$ a \emph{strongly fixed pair} if for every $b \in A$ we have $F_{\bar
@@
 In a preprocessing step we compute the trivial lower bound $S_0 =
-\sum_{u,v}\min(c(u,v),c(v,u))$ on the score.
+\sum_{u,v}\min(c(u,v),c(v,u))$ \cite[Lemma 4]{eades_median_2}\cite[Fact 3]{dujmovic_2004} on the score.
 We keep track of the score $S_P$ of the prefix and $S_{PT}=c(P, T)$ of

### 2024-09-20 tex/paper.tex
Minor changes to paper.tex.

@@
     r \in A$, with $m$ sitting between $b$ and its successor in $A$, and $l < (\supp(u) \cup
-    \supp(v)) < r$. Then let $X$ be connected to $l, m, r$. By choosing
+    \supp(v)) < r$ (see \cref{fig:blocking}). Then let $X$ be connected to $l, m, r$. By choosing
     the weights of $X$ appropriately, we can let both $r(X, v) = W_v r(X, \bar v)$ and $r(u, X)
@@
     v$ are not strongly fixed, one must consider features of the graph other than $u, v$ and
-    their neighbours, so indeed \cref{lem:sfp} is optimal. Note that this also applies in the unweighted case,
-    by taking $l, m, r$ to be sets of nodes rather than weighted single nodes.
+    their neighbours. In other words, \cref{lem:sfp} is optimal. Note that this remark also
+    applies in the unweighted case, by taking $l, m, r$ to be sets of nodes rather than
+    weighted single nodes.
 \end{remark}

### 2024-09-20 tex/paper.tex
More small changes.

@@
   reductions.
-  We apply these in our exact solver OCMu64, that directly uses branch-and-bound
+  We apply these in our exact solver \texttt{OCMu64}, that directly uses branch-and-bound
   on the ordering of the vertices of $B$ and does not depend on ILP or SAT
@@
 Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
-$(i, 1)$ and $(j,0)$ for components $A$ and $B$ respectively. The ordering of $A$
+$(i, 0)$ and $(j,1)$ for components $A$ and $B$ respectively. The ordering of $A$
 is fixed, and the goal is the find an ordering of $B$ that minimizes the number of
@@
 \caption{
-  Various examples where $u$ must come before $v$ ($u\b v$), where $u,v\in B$ can freely move around and
-  their neighbours in $A$ (on the dashed line) have fixed positions.}%
+  Various examples of $u, v \in B$, whose neighbors 
+  neighbours in $A$ (on the dashed line) have fixed positions.}%
 \label{fig}

### 2024-09-20 tex/paper.tex
Minor changes.

@@
     applies in the unweighted case, by taking $l, m, r$ to be sets of nodes rather than
-    weighted single nodes.
+    single nodes with weighted edges.
 \end{remark}
@@
 and $v$ always go right next to each other, and we can treat them as a single vertex. First,
-let us see that we cannot get `strong gluing' result analogous to \cref{lem:sfimplf}.
+let us see that we cannot get a `strong gluing' result analogous to \cref{lem:sfimplf}.
 

### 2024-09-26 tex/paper.tex
add lipics macros

@@
 \pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+%% \hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
 
@@
 
-%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line
+\titlerunning{OCMu64: a solver for One-sided Crossing Minimization}
 
@@
 
-\category{} %optional, e.g. invited paper
+\category{PACE Solver Description}
 
@@
 
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \EventEditors{John Q. Open and Joan R. Access}
-%% \EventNoEds{2}
-%% \EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-%% \EventShortTitle{CVIT 2016}
-%% \EventAcronym{CVIT}
-%% \EventYear{2016}
-%% \EventDate{December 24--27, 2016}
-%% \EventLocation{Little Whinging, United Kingdom}
-%% \EventLogo{}
-%% \SeriesVolume{42}
-%% \ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{\'{E}douard Bonnet and Pawe\l{} Rz\k{a}\.{z}ewski}
+\EventNoEds{2}
+\EventLongTitle{19th International Symposium on Parameterized and Exact Computation (IPEC 2024)}
+\EventShortTitle{IPEC 2024}
+\EventAcronym{IPEC}
+\EventYear{2024}
+\EventDate{September 4--6, 2024}
+\EventLocation{Royal Holloway, University of London, Egham, United Kingdom}
+\EventLogo{}
+\SeriesVolume{321}
+\ArticleNo{35}
 
